### 2023-05-12 paper.tex
started working on the paper within a tex workspace

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{multirow}
%\usepackage{multicol}

\title{ACARIS: Improving Conversational AI and Human Social Skills using User Embeddings}
\author{Simon Slamka}
\date{June 1, 2023}

\begin{document}

\maketitle

\begin{abstract}
In this paper, we propose ACARIS, the Advanced Communication Augmentor and Relational Insights System, a system utilizing a novel method to analyze emotional state, intent, and interest of text communication parties. ACARIS is being built with the goal of improving social skills of humans, while also improving the performance of human-facing AI systems. We go over our approach, including the initialization of user embeddings from message features, concatenation of user embeddings with word embeddings, modifications of the BERT architecture, and the training and evaluation processes. We also go over the results of our experiments, which demonstrate the effectiveness of our method.
\end{abstract}

\section{Keywords}
ACARIS, Conversational AI, Social Skills, User Embeddings, BERT, DistilBERT, Sentiment Analysis, Intent Classification, Emotion Recognition, Interest Recognition

\section{Definitions}
\begin{itemize}
	\item \textbf{ACARIS} - the Advanced Communication Augmentor and Relational Insights System
	\item \textbf{NLP} - Natural Language Processing - a subfield of linguistics, computer science, and artificial intelligence concerned with the interactions between computers and human language, in particular how to program computers to process and analyze large amounts of natural language data
	\item \textbf{Deep Learning} - a class of machine learning algorithms that uses multiple layers to progressively extract higher-level features from the raw input
	\item \textbf{SVM} - Support Vector Machine - a supervised machine learning model that uses classification algorithms for two-group classification problems
	\item \textbf{DT} - Decision Tree - 
	\item \textbf{LogReg} - Logistic Regression - a statistical model that in its basic form uses a logistic function to model a binary dependent variable, although many more complex extensions exist
	\item \textbf{RF} - Random Forest - an ensemble learning method for classification, regression and other tasks that operate by constructing a multitude of decision trees at training time and outputting the class that is the mode of the classes (classification) or mean prediction (regression) of the individual trees
	\item \textbf{TF-IDF} - Term Frequency - Inverse Document Frequency - a numerical statistic that is intended to reflect how important a word is to a document in a collection or corpus
	\item \textbf{the Transformer} - a deep learning model introduced in 2017, used primarily in the field of NLP
	\item \textbf{BERT} - Bidirectional Encoder Representations from Transformers - a transformer-based machine learning technique for natural language processing pre-training developed by Google
	\item \textbf{DistilBERT} - DistilBERT is a smaller, faster, cheaper version of BERT developed by HuggingFace
	\item \textbf{Vector} - a quantity that has both magnitude and direction
	\item \textbf{Vector Space} - a collection of vectors, which may be added together and multiplied ("scaled") by numbers, called scalars
	\item \textbf{Embedding Space} - a vector space with a coordinate for each word in the vocabulary, such that words that share common contexts in the corpus are located close to one another in the space
	\item \textbf{Word Embedding} - A vector representation of a word's meaning
	\item \textbf{User Embedding} - A vector representation of a user's personality, emotional state, intent, and interest
	\item \textbf{ReLU} - Rectified Linear Unit - an activation function that returns the input value if it is positive, otherwise it returns zero
	\item \textbf{Loss} - a number indicating how bad the model's prediction was on a single example
	\item \textbf{Loss Gradient} - the gradient of the loss with respect to the model parameters
	\item \textbf{Ablation Study} - a study in which specific components of a system are removed to analyze their impact on the overall performance

\section{Motivation and Premise}
I've always had an issue with interpersonal relationships. I could never fully understand the way people work on a social level. I understand the technical and biological fundamentals, and superficially, how the mind works, but not how all this becomes so much more complex when actually talking and dealing with people. Sometimes, I feel that another person and I broadcast on different frequencies, because we are unable to either understand one another or maintain a (romantic) relationship for an extended period of time. I have tried for many years to find a technical solution to this problem, but only after coming to Denmark, I acquired the core knowledge to try and accomplish this ambitious goal by really getting into it and self-studying as much as I could.\\
I firmly believe that all things in nature are governed by rules and these rules can be observed, measured, and then, based on that data, predicted. This includes human behavior and emotions. We’re nothing more than complex electrobiochemical machines driven by electrical impulses and hormones. Apart from that, even if we don’t understand our own minds yet, we still have many, many years of knowledge about how human personalities work and how we make decisions based on what happens to or around us. On a fundamental level, this doesn’t change. Sure, they say that we’re all different. However, the core remains. We all share many attributes that make us human. I believe that we, given enough data, can use these attributes to predict human behavior, reactions, emotional state, and intent.

\section{Hypothesis}
Given enough conversational data per person, human behavior (emotional state, intent) in text communication can be predicted with a high level of confidence ($>80\%$) due to the fact that humans are, on a fundamental level, very similar to one another.

%\begin{multicols}{2}
\section{Introduction}
Interpersonal communication has always been an integral part of human lives. With the rise of the Internet and, subsequently, social media and other forms of online text communication, the manner in which we talk has changed dramatically. This has led to a drop in social skills in humans, particularly those of the last generation. ACARIS attempts to adjust for this by providing a way to analyze the emotional state, intent, and interest of text communication parties, providing them with a way to improve their social skills, while also improving the performance of conversational AI systems, which are becoming increasingly prevalent in our society, and their ability to understand human emotions, intent, and interest is becoming more and more important, especially in AI systems that directly interact with humans, such as digital assistants, chatbots, and others.

\section{Literature Review and Related Work}
\subsection{Studied Literature}
\subsubsection{Human Emotions}
\begin{itemize}
	\item 
\end{itemize}
\subsubsection{Sentiment Analysis}
\begin{itemize}
	\item \textbf{Machine Learning with PyTorch and Scikit-Learn} by Yuxi Liu, Vahid Mirjalili, Sebastian Raschka
	\item \textbf{Hands-on Machine Learning with Scikit-Learn, Keras, and TensorFlow} by Aurélien Géron
\end{itemize}

\section{Initial Attempts}
Our initial attempts of implementing ACARIS included the use of SVMs, DTs, LogReg, and RFs, each paired with TF-IDF in the preprocessing stage. None of these methods have proven to be accurate enough (barely reaching 50\% accuracy) for large amounts of complex language, especially casual language that often includes slang, sarcasm, emoji, and similar elements. The primary issue was the lack of these methods' ability to capture semantical and contextual aspects of our dataset. Another issue was TF-IDF's lack of word order understanding. Knowing that the Transformer architecture is capable of capturing these aspects due to its positional encodinds and self-attention mechanism, we decided to use it as the basis for ACARIS.

\section{Methodology}
In this section, we provide a detailed description of our approach, including the initialization of user embeddings, concatenation with word embeddings, modifications to the model architecture, and the training and evaluation processes.

\subsection{User Embeddings Initialization}
For each user $u$, we create an initial user embedding $e_u$ of size $d_e$, where $d_e$ is the dimensionality of the user embeddings. We initialize $e_u$ with random values sampled from a Gaussian distribution:
\begin{equation}
\begin{aligned}
&\text{\texttt{from torch import randn}} \\
&e_u = \text{\texttt{randn}}(d_e)
\end{aligned}
\end{equation}

\subsection{Concatenation of User and Word Embeddings}
Given a message $w$ (converted to a word embedding) with its word embedding $e_w$ (of size $d_m$) from a BERT-like pre-trained model such as DistilBERT, we concatenate the user embedding $e_u$ to the word embedding $e_w$ to create a joint representation $e_\textnormal{joint}$ (of size $d_e + d_m$):
\begin{equation}
\begin{aligned}
&\text{\texttt{from torch import cat}} \\
&e_\textnormal{joint} = \textnormal{\texttt{cat}}([e_u, e_w], \textnormal{dim}=-1)
\end{aligned}
\end{equation}

\subsection[Model Architecture Modification]{Model Architecture\\ Modification}
To accommodate the concatenated embeddings, we create a custom input layer with the new input size $d_e + d_m$ within a BERT-flavored model. An alternative could be to use a separate fully-connected layer (with ReLU activation) to map the concatenated embeddings to a compatible size:
\begin{equation}
\begin{aligned}
&\text{\texttt{from torch import randn}} \\
&\text{\texttt{from torch import relu}} \\
&\text{\texttt{from torch import matmul}} \\
&W1 = \text{\texttt{randn}}((d_e + d_m, d_m)) \\
&b1 = \text{\texttt{randn}}(d_m) \\
&e_\textnormal{map} = \text{\texttt{relu}}(\text{\texttt{matmul}}(e_\textnormal{joint}, W1) + b1)
\end{aligned}
\end{equation}
Then, pass $e_\textnormal{map}$ through the existing model architecture.

\subsection[Training with User Embeddings]{Training with\\ User Embeddings}
We train the model with the concatenated embeddings, which involves modifying the training loop to include user embeddings for each message. For each training step, we fetch the corresponding user embeddings, concatenate them with word embeddings, and pass the result to the model. The model learns to associate user-specific patterns with the message content.

\subsection[Updating User Embeddings]{Updating User\\ Embeddings}
To update user embeddings over time, we backpropagate the gradients from the model loss to the user embeddings. This requires a custom training loop to ensure that the gradients are properly propagated. Alternatively, we can consider methods like moving averages or other heuristics to update the embeddings based on new interactions.

For example, if using gradient descent, the user embedding update could look like this:

\begin{equation}
e_u = e_u - \text{lr} \cdot \frac{\partial L}{\partial e_u}
\end{equation}
where $\frac{\partial L}{\partial e_u}$ is the gradient of the loss with respect to the user embedding $e_u$ and $\text{lr}$ is the learning rate.

\section{Evaluation}
We evaluate our approach using benchmark datasets for various conversational AI tasks, such as sentiment analysis and intent classification. We compare the performance of models trained with and without user embeddings to demonstrate the effectiveness of our method. We also perform ablation studies to analyze the impact of various components, such as the user embedding size and update methods.

\section{Results}
NaN

\section{Conclusion}
NaN

%\end{multicols}

\end{document}

### 2023-05-12 datToCsv.py

@@ -1,0 +1,15 @@
+import csv
+
+dat_file = "file.dat"
+csv_file = "file.csv"
+
+with open(dat_file, "r") as input_file, open(csv_file, "w", newline='') as output_file:
+    writer = csv.writer(output_file, delimiter='|')
+    writer.writerow(["uid", "timestamp", "content"])
+    for line in input_file:
+        parts = line.strip().split(" :: ")
+        timestamp = parts[0]
+        uid_content = parts[1].split(": ")
+        uid = uid_content[0]
+        content = uid_content[1]
+        writer.writerow([uid, timestamp, content])

### 2023-05-12 dataAnal.py

@@ -15,7 +15,7 @@ userTopics = {}
 def get_user_msgs(userID, csvPath):
 	msgs = []
 	with open(csvPath, "r") as f_in:
-		reader = csv.reader(f_in, delimiter=",")
+		reader = csv.reader(f_in, delimiter="|")
 		for row in reader:
 			if row[0] == userID:
 				msgs.append(row[2])
@@ -27,7 +27,7 @@ def preprocess_msgs(msgs):
 	processedMsgs = []
 	for msg in msgs:
 		words = re.findall(r"\b(?!\d+\b)\w+\b", msg)
-		words = [word.lower() for word in words if word.lower() not in stopWords and "smiling" not in word.lower() and "eyes" not in word.lower() and "face" not in word.lower() and "https" not in word.lower() and "grinning" not in word.lower()]
+		words = [word.lower() for word in words if word.lower() not in stopWords and "smiling" not in word.lower() and "eyes" not in word.lower() and "face" not in word.lower() and "https" not in word.lower() and "grinning" not in word.lower() and "clyde" not in word.lower() and "unclyde" not in word.lower()]
 		processedMsgs.append(words)
 	return processedMsgs
 
@@ -65,7 +65,7 @@ def get_user_topics(lda, dict, stopWords, processedMsgs):
 def get_most_common_sentiment(userID, csvPath):
 	sents = []
 	with open(csvPath, "r") as f_in:
-		reader = csv.reader(f_in, delimiter=",")
+		reader = csv.reader(f_in, delimiter="|")
 		for row in reader:
 			if row[0] == userID:
 				sents.append(row[3])
@@ -83,7 +83,10 @@ def generate_wordcloud(processedMsgs):
 
 def main():
 	stopw = set(stopwords.words("english"))
-	msgs = get_user_msgs("Reknez#9257", "sents_merged.csv")
+	#msgs = get_user_msgs("Reknez#9257", "./datasets/sentAnal/sents_merged_sents_merged_cleaned_expanded.csv")
+	msgs = get_user_msgs("simtoon", "./datasets/sentAnal/sents_merged_cleaned_expanded.csv")
+	# msgs = get_user_msgs("Clyde#0000", "./datasets/sentAnal/sents_merged_cleaned_expanded.csv")
+	#msgs = get_user_msgs("Reknez#9257", "./datasets/sentAnal/sents_merged_cleaned_expanded.csv")
 	processedMsgs = preprocess_msgs(msgs)
[…]

### 2023-05-12 emo.py

@@ -89,10 +89,10 @@ class emo:
         self.model.fit(x, y) # run training on the sole-member batch
 
 emo_mdl = emo() # instantiate the class
-with open("./datasets/cleanedMsg/msgLog.csv", "r") as f: # open the input file
-    reader = csv.DictReader(f, delimiter=",", fieldnames=["uid", "timestamp", "content"])
+with open("./datasets/msgsNew.csv", "r") as f: # open the input file
+    reader = csv.DictReader(f, delimiter="|", fieldnames=["uid", "timestamp", "content"])
 
-    with open("./datasets/emoAnalyzedAndClean/msgLog.csv", "w", newline="") as out:
+    with open("./datasets/msgsNewLabeled.csv", "w", newline="") as out:
         fieldnames = ["uid", "timestamp", "content", "sentiment"]
         writer = csv.DictWriter(out, fieldnames=fieldnames, delimiter="|")
         writer.writeheader()

### 2023-05-12 emoToSent.py

@@ -31,7 +31,7 @@ emoToSent = {
     "neutral": "neu"
 }
 
-with open("./datasets/emoAnalyzedAndClean/msgLog.csv", "r") as f_in, open("./datasets/sentAnal/sents.csv", "w", newline="") as f_out:
+with open("./datasets/msgsNewLabeled.csv", "r") as f_in, open("./datasets/sentAnal/sents.csv", "w", newline="") as f_out:
 	reader = csv.reader(f_in, delimiter="|")
 	writer = csv.writer(f_out, delimiter="|")
 	for row in reader:

### 2023-05-12 feature_extract.py

@@ -128,16 +128,21 @@ class FeatExtractor:
 
 	def txt_to_csv(self, txtPath, csvPath, soughtUser):
 		pattern = r"(\d{4}-\d{2}-\d{2} \d{2}:\d{2}:\d{2}\.\d{6}):: .+\/(.+?): (.+)"
+		alsoPattern = r"^(\d{4}-\d{2}-\d{2}\s\d{2}:\d{2}:\d{2})\s::\s([\w#]+):\s(.+)$"
 		with open(txtPath, "r") as infile, open(csvPath, "w") as outfile:
-			writer = csv.DictWriter(outfile, fieldnames=["timestamp", "uid", "content"])
+			writer = csv.DictWriter(outfile, fieldnames=["uid", "timestamp", "content"], delimiter="|")
 			writer.writeheader()
 
 			for line in infile:
 				match = re.match(pattern, line)
+				alsoMatch = re.match(alsoPattern, line)
 				if match:
 					timestamp, discordTag, content = match.groups()
-					#if "The Butler#5636" not in discordTag and "MarkTheBot#5636" not in discordTag:
-					if soughtUser in discordTag:
+					if "The Butler#5636" not in discordTag and "MarkTheBot#5636" not in discordTag:
+						writer.writerow({"uid": discordTag, "timestamp": timestamp, "content": content})
+				elif alsoMatch:
+					timestamp, discordTag, content = alsoMatch.groups()
+					if "The Butler#5636" not in discordTag and "MarkTheBot#5636" not in discordTag:
 						writer.writerow({"uid": discordTag, "timestamp": timestamp, "content": content})
 		print(f"Saved {csvPath}")
 
@@ -359,13 +364,13 @@ if __name__ == "__main__":
 	mdl = "distilbert-base-uncased"
 	extractor = FeatExtractor(mdl)
 
-	# if os.path.splitext("./datasets/msgs.txt")[1] == ".txt":
-	#     txt_to_csv("./datasets/msgs.txt", "./datasets/msgs.csv", args.uid)
+	if os.path.splitext("./datasets/messagesNew.txt")[1] == ".txt":
+		extractor.txt_to_csv("./datasets/messagesNew.txt", "./datasets/msgsNew.csv", args.uid)
 
-	msgs = extractor.read_msgs_from_file("./datasets/sentAnal/sents_merged_cleaned.csv")
-	print(msgs[0].keys())
[…]

### 2023-05-12 mergeDatasets.py

@@ -1,0 +1,9 @@
+import pandas as pd
+
+df1 = pd.read_csv("./datasets/sentAnal/sents_merged_cleaned.csv", encoding="utf-8", delimiter="|")
+df2 = pd.read_csv("./datasets/sentAnal/sents_merged.csv", encoding="utf-8", delimiter="|")
+
+merged = pd.concat([df1, df2], ignore_index=True)
+
+# only do this if headers match !!! jackass LOL
+merged.to_csv("./datasets/sentAnal/sents_merged_cleaned_expanded.csv", index=False, sep="|")

### 2023-05-12 mergeUsers.py

@@ -10,7 +10,8 @@ smtnUsernames = {
 	"Princess4h3g4oUS#0001": "simtoon",
 	"TheKentuckian#6304": "simtoon",
 	"J3ff#0001": "simtoon",
-	"DerFeuchteGigachad#8218": "simtoon"
+	"DerFeuchteGigachad#8218": "simtoon",
+	"yoyo20432930#9910": "simtoon"
 }
 
 with open("./datasets/sentAnal/sents.csv", "r") as f_in, open("./datasets/sentAnal/sents_merged.csv", "w", newline="") as f_out:

### 2023-05-12 removeURLandtags.py

@@ -1,0 +1,37 @@
+import pandas as pd
+import re
+import numpy as np
+
+# Load the dataset into a pandas DataFrame
+df = pd.read_csv('./datasets/sentAnal/sents_merged_cleaned_expanded.csv', sep="|")
+
+# Define regular expressions to match URLs and Discord mentions
+url_pattern = r'http[s]?://(?:[a-zA-Z]|[0-9]|[$-_@.&+]|[!*\\(\\),]|(?:%[0-9a-fA-F][0-9a-fA-F]))+'
+mention_pattern = re.compile(r'<@\!?(\d+)>')
+
+def remove_patterns(text, patterns):
+    for pattern in patterns:
+        text = re.sub(pattern, '', text)
+    return text
+
+df['content'] = df['content'].astype(str)
+
+df['content'] = df['content'].apply(lambda text: remove_patterns(text, [url_pattern, mention_pattern]))
+
+df['content'].replace('', np.nan, inplace=True)
+
+df.dropna(subset=['content'], inplace=True)
+
+# # Define a function to remove URLs and Discord mentions from a string
+# def remove_urls_and_mentions(text):
+#     if text is not None and isinstance(text, str):
+#         text = re.sub(url_pattern, '', text)
+#         text = re.sub(mention_pattern, '', text)
+#         return text.strip()
+#     else:
+#         return text
+
+# # Apply the function to the "content" column of the DataFrame
+# df['content'] = df['content'].apply(remove_urls_and_mentions)
+
+df.to_csv('./datasets/sentAnal/cleared.csv', sep='|', index=False)

### 2023-05-12 trainDistilBERT.py

@@ -10,14 +10,15 @@ from datasets import load_dataset, Dataset
 import pandas as pd
 from sklearn.metrics import accuracy_score, precision_recall_fscore_support
 import wandb
+import huggingface_hub
 
 config = {
 	"mdl": "distilbert-base-uncased",
 	"epochs": 5,
 	"batchSize": 12,
     "maxLen": 512,
-    "warmupSteps": 500,
-    "weightDecay": 0.01,
+    "warmupSteps": 750,
+    "weightDecay": 0.02,
 	"outputDir": "./output",
     "earlyStopping": True,
     "earlyStoppingPatience": 2,
@@ -33,7 +34,7 @@ class ACARISBERT:
         self.trainPath = trainPath
         self.valPath = valPath
         self.tokenizer = DistilBertTokenizerFast.from_pretrained(config["mdl"])
-        self.model = DistilBertForSequenceClassification.from_pretrained(config["mdl"], num_labels=3)
+        self.model = DistilBertForSequenceClassification.from_pretrained(config["mdl"], num_labels=3, dropout=config["dropout"], attention_dropout=config["dropout"])
         
     def read_data(self, path):
         df = pd.read_csv(path, sep="|", usecols=["content", "sentiment"])
@@ -84,15 +85,13 @@ class ACARISBERT:
             weight_decay=config["weightDecay"],
             logging_dir="./logs",
             logging_steps=100,
+            learning_rate=2e-5,
             evaluation_strategy="epoch",
             save_strategy="epoch",
             load_best_model_at_end=True,
             metric_for_best_model="accuracy",
             save_total_limit=5,
-            push_to_hub=True,
-            push_to_hub_organization="ongknsro",
-			push_to_hub_model_id="ACARIS-wordEmbOnly-dsc-sent_DistilBERT",
-            hub_strategy="checkpoint"
+            fp16=True,
         )
         
         trainer = Trainer(
@@ -100,7 +99,6 @@ class ACARISBERT:
             args=trainingArgs,
             train_dataset=trainDS,
             eval_dataset=valDS,
-            dropout=config["dropout"],
             compute_metrics=self.compute_metrics,
             callbacks=[EarlyStoppingCallback(early_stopping_patience=config["earlyStoppingPatience"])]
         )
@@ -112,5 +110,4 @@ class ACARISBERT:
 if __name__ == "__main__":
[…]

### 2023-05-15 paper.tex
expanded sent dataset significantly, cleaned up, merged with orig, and split into splits

@@
 \usepackage{multirow}
+\usepackage[backend=biber, sorting=none]{biblatex}
+\addbibresource{refs.bib}
 %\usepackage{multicol}
@@
 	\item \textbf{TF-IDF} - Term Frequency - Inverse Document Frequency - a numerical statistic that is intended to reflect how important a word is to a document in a collection or corpus
-	\item \textbf{the Transformer} - a deep learning model introduced in 2017, used primarily in the field of NLP
-	\item \textbf{BERT} - Bidirectional Encoder Representations from Transformers - a transformer-based machine learning technique for natural language processing pre-training developed by Google
-	\item \textbf{DistilBERT} - DistilBERT is a smaller, faster, cheaper version of BERT developed by HuggingFace
+	\item \textbf{the Transformer} - a deep learning model introduced in 2017, used primarily in the field of NLP\cite{vaswani2017attention}
+	\item \textbf{BERT} - Bidirectional Encoder Representations from Transformers - a transformer-based machine learning technique for natural language processing pre-training developed by Google\cite{devlin2019bert}
+	\item \textbf{DistilBERT} - DistilBERT is a smaller, faster, cheaper version of BERT developed by HuggingFace\cite{sanh2020distilbert}
 	\item \textbf{Vector} - a quantity that has both magnitude and direction
@@
 	\item \textbf{Loss} - a number indicating how bad the model's prediction was on a single example
-	\item \textbf{Loss Gradient} - the gradient of the loss with respect to the model parameters
+	\item \textbf{Cross-Entropy Loss} - a loss function used for classification problems
+	\item \textbf{Adam} - an optimization algorithm that can be used instead of the classical stochastic gradient descent procedure to update network weights
 	\item \textbf{Ablation Study} - a study in which specific components of a system are removed to analyze their impact on the overall performance
-
+\end{itemize}
 \section{Motivation and Premise}
@@
 
-\section{Literature Review and Related Work}
-\subsection{Studied Literature}
-\subsubsection{Human Emotions}
+\subsection{Literature Review and Related Work}
+\subsubsection{Studied Literature}
 \begin{itemize}
-	\item 
-\end{itemize}
-\subsubsection{Sentiment Analysis}
-\begin{itemize}
-	\item \textbf{Machine Learning with PyTorch and Scikit-Learn} by Yuxi Liu, Vahid Mirjalili, Sebastian Raschka
-	\item \textbf{Hands-on Machine Learning with Scikit-Learn, Keras, and TensorFlow} by Aurélien Géron
+	\item \textbf{Machine Learning with PyTorch and Scikit-Learn}\cite{raschka2022machine} by Yuxi Liu, Vahid Mirjalili, Sebastian Raschka
+	\item \textbf{Hands-on Machine Learning with Scikit-Learn, Keras, and TensorFlow}\cite{geron2022hands} by Aurélien Géron
 \end{itemize}
 
-\section{Initial Attempts}
+\subsection{Initial Attempts}
 Our initial attempts of implementing ACARIS included the use of SVMs, DTs, LogReg, and RFs, each paired with TF-IDF in the preprocessing stage.
@@
 Another issue was TF-IDF's lack of word order understanding.
-Knowing that the Transformer architecture is capable of capturing these aspects due to its positional encodinds and self-attention mechanism, we decided to use it as the basis for ACARIS.
+Knowing that the Transformer\cite{vaswani2017attention} architecture is capable of capturing these aspects due to its positional encodinds and self-attention mechanism, we decided to use it as the basis for ACARIS.
+
+\subsection{Short Intro on Transformers}
+The Transformer\cite{vaswani2017attention} is a deep learning model proposed in 2017 by a team of Google Brain researchers.
+It is mainly used in NLP, but it has also found its way into numerous vision projects (Latent Diffusion\cite{rombach2021highresolution}/Stable Diffusion/LLaVA\cite{liu2023visual}, to name a few).
 
 \section{Methodology}
-In this section, we provide a detailed description of our approach, including the initialization of user embeddings, concatenation with word embeddings, modifications to the model architecture, and the training and evaluation processes.
+In this section, we provide a detailed description of our approach, including the computation of user embeddings, concatenation with word embeddings, modifications to the model architecture, and the training and evaluation processes.
+
+% features:
+% - Mean wordcount (per msg)
+% - Vocab richness (type-token ratio?) - Unique words / total words
+% - Mean emoji count (per msg)
+% - Mean emoticon count (per msg)
+% - Mean punctuation count (per msg)
+% - Mean sentiment score (per msg)
+% - Dominant/prevalent topics
+% - Mean response time (!exclude closing messages, such as "Goodnight")
+% - Mean message count (per day)
+% - Mean links (per msg)
+% - Mean markdown code snippet sections (per msg)
+% - Mean abbreviations and acronyms (per msg) (such as "lol", "omg", "FBI", ...)
+% - Mean hashtag count (per msg)
+
+\subsection{Dataset}
+To build our dataset, we collected 100 thousand messages from our Discord server, classified them into 3 classes (pos, neg, neu), and augmented them with the GoEmotions\cite{demszky2020goemotions} dataset, which contains 58 thousand messages classified into 27 classes.
+We squashed the 27 classes into 3 classes (pos, neg, neu) and concatenated the two datasets.
+To minimize error caused by input data, we removed all users with less than 25 messages, URLs, markdown code blocks, Discord mentions and custom emoji, and attachments.
+The resulting dataset was split into 85\% training, 10\% validation, and 5\% test sets.
 
 \subsection{User Embeddings Initialization}
-For each user $u$, we create an initial user embedding $e_u$ of size $d_e$, where $d_e$ is the dimensionality of the user embeddings.
-We initialize $e_u$ with random values sampled from a Gaussian distribution:
+For each user $u$, we loop through all messages $m$ sent by $u$ and extract these features:
+\begin{itemize}
+	\item \textbf{Mean word count (per all $m$)} - \(\overline{w} = \frac{1}{N} \sum_{i=1}^{N} w_i \), where $w_i$ is the word count of $i$-th message and $N$ is the total number of messages
+	\item \textbf{Vocabulary richness (per all $m$)} - \(r = \frac{U}{W} \), where $U$ is the number of unique words and $W$ is the total number of words
+	\item \textbf{Mean emoji count (per all $m$)} - \(\overline{e} = \frac{1}{N} \sum_{i=1}^{N} e_i \), where $e_i$ is the emoji count of $i$-th message and $N$ is the total number of messages
+	\item \textbf{Mean emoticon count (per all $m$)} - \(\overline{em} = \frac{1}{N} \sum_{i=1}^{N} em_i \), where $e_i$ is the emoticon count of $i$-th message and $N$ is the total number of messages
+	\item \textbf{Mean punctuation count (per all $m$)} - \(\overline{p} = \frac{1}{N} \sum_{i=1}^{N} p_i \), where $p_i$ is the punctuation count of $i$-th message and $N$ is the total number of messages
+	\item \textbf{Mean sentiment score (per all $m$)} - \(\overline{s} = \frac{1}{N} \sum_{i=1}^{N} s_i \), where $s_i$ is the sentiment score of $i$-th message and $N$ is the total number of messages
+	\item \textbf{Dominant/prevalent topics (per all $m$)} - the most common topics in all messages
+	\item \textbf{Mean response time (per all $m$)} - \(\overline{r} = \frac{1}{N} \sum_{i=1}^{N} r_i \), where $r_i$ is the response time of $i$-th message and $N$ is the total number of messages
+	\item \textbf{Mean message count (per day)} - \(\overline{m} = \frac{1}{D} \sum_{i=1}^{D} m_i \), where $m_i$ is the message count of $i$-th day and $D$ is the total number of days
+	\item \textbf{Mean links (per all $m$)} - \(\overline{l} = \frac{1}{N} \sum_{i=1}^{N} l_i \), where $l_i$ is the link count of $i$-th message and $N$ is the total number of messages
+	\item \textbf{Mean markdown code snippet sections (per all $m$)} - \(\overline{c} = \frac{1}{N} \sum_{i=1}^{N} c_i \), where $c_i$ is the markdown code snippet section count of $i$-th message and $N$ is the total number of messages
+	\item \textbf{Mean abbreviations and acronyms (per all $m$)} - \(\overline{a} = \frac{1}{N} \sum_{i=1}^{N} a_i \), where $a_i$ is the abbreviation and acronym count of $i$-th message and $N$ is the total number of messages
+	\item \textbf{Mean hashtag count (per all $m$)} - \(\overline{h} = \frac{1}{N} \sum_{i=1}^{N} h_i \), where $h_i$ is the hashtag count of $i$-th message and $N$ is the total number of messages
+\end{itemize}
+Then, we concatenate all the features into a single vector $e_u$ (of size $d_e$):
 \begin{equation}
 \begin{aligned}
-&\text{\texttt{from torch import randn}} \\
-&e_u = \text{\texttt{randn}}(d_e)
+&\text{\texttt{from torch import cat}} \\
+&e_u = \textnormal{\texttt{cat}}([\overline{w}, r, \overline{e}, \overline{em}, \overline{p}, \overline{s}, \overline{r}, \overline{m}, \overline{l}, \overline{c}, \overline{a}, \overline{h}], \textnormal{dim}=-1)
 \end{aligned}
 \end{equation}
-
 \subsection{Concatenation of User and Word Embeddings}
-Given a message $w$ (converted to a word embedding) with its word embedding $e_w$ (of size $d_m$) from a BERT-like pre-trained model such as DistilBERT, we concatenate the user embedding $e_u$ to the word embedding $e_w$ to create a joint representation $e_\textnormal{joint}$ (of size $d_e + d_m$):
+Given a message $m$ with its word embedding $e_w$ (of size $d_m$) from a BERT-like pre-trained model, which, in our case, was DistilBERT\cite{sanh2020distilbert}, we concatenate the user embedding $e_u$ to the word embedding $e_w$ to create a joint representation $e_\textnormal{joint}$ (of size $d_e + d_m$):
 \begin{equation}
@@
 
-\subsection[Model Architecture Modification]{Model Architecture\\ Modification}
+\subsection{Model Architecture Modification}
 To accommodate the concatenated embeddings, we create a custom input layer with the new input size $d_e + d_m$ within a BERT-flavored model.
-An alternative could be to use a separate fully-connected layer (with ReLU activation) to map the concatenated embeddings to a compatible size:
+An alternative that we thought of using was to use a separate fully-connected layer (with ReLU activation) to map the concatenated embeddings to a compatible size:
 \begin{equation}
@@
 
-\subsection[Training with User Embeddings]{Training with\\ User Embeddings}
-We train the model with the concatenated embeddings, which involves modifying the training loop to include user embeddings for each message.
-For each training step, we fetch the corresponding user embeddings, concatenate them with word embeddings, and pass the result to the model.
-The model learns to associate user-specific patterns with the message content.
+\subsection{Training with User Embeddings}
+For each training step, we pass the concatenated embeddings $e_\textnormal{joint}$ through the model and compute the cross-entropy loss $L$.
+Then, we backpropagate the gradients from the loss to the model parameters and update the parameters using Adam.
+The model thus learns to associate every message $m$ with a user embedding $e_u$ and a sentiment label $y$.
 
-\subsection[Updating User Embeddings]{Updating User\\ Embeddings}
-To update user embeddings over time, we backpropagate the gradients from the model loss to the user embeddings.
-This requires a custom training loop to ensure that the gradients are properly propagated.
-Alternatively, we can consider methods like moving averages or other heuristics to update the embeddings based on new interactions.
-
-For example, if using gradient descent, the user embedding update could look like this:
-
-\begin{equation}
-e_u = e_u - \text{lr} \cdot \frac{\partial L}{\partial e_u}
-\end{equation}
-where $\frac{\partial L}{\partial e_u}$ is the gradient of the loss with respect to the user embedding $e_u$ and $\text{lr}$ is the learning rate.
+\subsection{Updating User Embeddings}
+The user embeddings $e_u$ are not updated during training.
+Instead, they are pre-computed during data preprocessing and stored in an embedding matrix.
+We repeat training every week, using new data from the previous week to update the user embeddings $e_u$.
+The reason for this decision is that we want the user embeddings $e_u$ in a static state to prevent any potential issues with losses.
+We considered updating the user embeddings $e_u$ during training, but we decided against it because we believe that it would be too computationally expensive and would not provide any significant benefits.
+It could actually worsen the model's performance, as the user embeddings $e_u$ would be constantly changing, which could lead to the model being unable to learn to associate messages $m$ with user embeddings $e_u$.
 
 \section{Evaluation}
-We evaluate our approach using benchmark datasets for various conversational AI tasks, such as sentiment analysis and intent classification.
-We compare the performance of models trained with and without user embeddings to demonstrate the effectiveness of our method.
-We also perform ablation studies to analyze the impact of various components, such as the user embedding size and update methods.
+NaN
 
+\section{Validation}
+To validate our approach, we compared the performance of our model with the performance of a baseline model.
+We used the same model, DistilBERT, but without the user embeddings $e_u$.
+We fine-tuned both models on the same dataset and compared their performance on the same test set.
 \section{Results}
@@
 
+\printbibliography
+
 %\end{multicols}

### 2023-05-15 data_loader.py

@@ -27,7 +27,8 @@ def split_data(data, trainRatio, valRatio):
 
 	dropped = 0
 
-	data.columns = ["uid", "timestamp", "content", "sentiment"]
+	# data.columns = ["uid", "timestamp", "content", "sentiment"]
+	data.columns = ["uid", "content", "sentiment"]
 
 	try:
 		data = data.drop(columns=["nan"])
@@ -56,4 +57,5 @@ def split_data(data, trainRatio, valRatio):
 	print(f"Dropped {dropped} rows")
 
 if __name__ == "__main__":
-	split_data("./datasets/sentAnal/sents_merged_cleaned.csv", 0.75, 0.1)
+	#split_data("./datasets/sentAnal/sents_merged_cleaned.csv", 0.75, 0.1)
+	split_data("./datasets/all_noTimestamps.csv", 0.75, 0.1)

### 2023-05-15 goemotionsMerge.py

@@ -1,0 +1,47 @@
+import csv
+
+dataset = []
+with open('./datasets/go_emotions_dataset.csv', 'r') as file:
+    reader = csv.DictReader(file)
+    for row in reader:
+        dataset.append(row)
+
+def merge_labels(row):
+    emotions = ['admiration', 'amusement', 'anger', 'annoyance', 'approval', 'caring', 'confusion',
+                'curiosity', 'desire', 'disappointment', 'disapproval', 'disgust', 'embarrassment',
+                'excitement', 'fear', 'gratitude', 'grief', 'joy', 'love', 'nervousness', 'optimism',
+                'pride', 'realization', 'relief', 'remorse', 'sadness', 'surprise', 'neutral']
+
+    pos_emotions = ['admiration', 'amusement', 'approval', 'caring', 'curiosity', 'excitement',
+                    'gratitude', 'joy', 'love', 'optimism', 'pride', 'realization', 'relief', 'surprise']
+
+    neg_emotions = ['anger', 'annoyance', 'disappointment', 'disapproval', 'disgust', 'embarrassment',
+                    'fear', 'grief', 'remorse', 'sadness']
+
+    pos_count = sum(int(row[emotion]) for emotion in pos_emotions)
+    neg_count = sum(int(row[emotion]) for emotion in neg_emotions)
+    neu_count = int(row['neutral'])
+
+    if pos_count > neg_count and pos_count > neu_count:
+        row['sentiment'] = 'pos'
+    elif neg_count > pos_count and neg_count > neu_count:
+        row['sentiment'] = 'neg'
+    else:
+        row['sentiment'] = 'neu'
+
+    for emotion in emotions:
+        del row[emotion]
+
+    del row['example_very_unclear']
+
+    return row
+
+for i, row in enumerate(dataset):
+    dataset[i] = merge_labels(row)
+
+fieldnames = dataset[0].keys()
+
+with open('./datasets/go_merged.csv', 'w', newline='') as file:
+    writer = csv.DictWriter(file, fieldnames=fieldnames, delimiter='|')
+    writer.writeheader()
+    writer.writerows(dataset)

### 2023-05-18 paper.tex
further progress, almost established a baseline; made source data more robust

@@
 \title{ACARIS: Improving Conversational AI and Human Social Skills using User Embeddings}
-\author{Simon Slamka}
+\author{Simon Slamka\\
+\small\textbf{OngakkenAI}}
 \date{June 1, 2023}
@@
 
-\section{Keywords}
+\section{Introduction}
+\subsection{Keywords}
 ACARIS, Conversational AI, Social Skills, User Embeddings, BERT, DistilBERT, Sentiment Analysis, Intent Classification, Emotion Recognition, Interest Recognition
 
-\section{Definitions}
+\subsection{Definitions}
 \begin{itemize}
@@
 	\item \textbf{TF-IDF} - Term Frequency - Inverse Document Frequency - a numerical statistic that is intended to reflect how important a word is to a document in a collection or corpus
-	\item \textbf{the Transformer} - a deep learning model introduced in 2017, used primarily in the field of NLP\cite{vaswani2017attention}
-	\item \textbf{BERT} - Bidirectional Encoder Representations from Transformers - a transformer-based machine learning technique for natural language processing pre-training developed by Google\cite{devlin2019bert}
+	\item \textbf{the Transformer} - a deep learning architecture introduced in 2017, used primarily in the field of NLP\cite{vaswani2017attention}
+	\item \textbf{BERT} - Bidirectional Encoder Representations from Transformers - a transformer-based machine learning model for natural language processing pre-training developed by Google\cite{devlin2019bert}
 	\item \textbf{DistilBERT} - DistilBERT is a smaller, faster, cheaper version of BERT developed by HuggingFace\cite{sanh2020distilbert}
@@
 \end{itemize}
-\section{Motivation and Premise}
+\subsection{Motivation}
 I've always had an issue with interpersonal relationships.
@@
 
-\section{Hypothesis}
+\subsection{Hypothesis}
 Given enough conversational data per person, human behavior (emotional state, intent) in text communication can be predicted with a high level of confidence ($>80\%$) due to the fact that humans are, on a fundamental level, very similar to one another.
 
+Additionally, we posit that person-specific performance improvements can be achieved by individualizing predictions by using a unique vector representation of a person's personality, emotional state, intent, and interest, which we call a user embedding.
+The postulate stems in the core concept of neural networks being universal function approximators.
+Therefore, in theory, a neural network should be able to learn to associate a user embedding with a person's behavior in text communication and use that information to improve its predictions.
+
 %\begin{multicols}{2}
-\section{Introduction}
-Interpersonal communication has always been an integral part of human lives.
+\subsection{Premise}
+Interpersonal communication has always been an integral part of human lives and is critical from the moment we're born.
 With the rise of the Internet and, subsequently, social media and other forms of online text communication, the manner in which we talk has changed dramatically.
@@
 	\item \textbf{Hands-on Machine Learning with Scikit-Learn, Keras, and TensorFlow}\cite{geron2022hands} by Aurélien Géron
+	\item \textbf{Transformers for Natural Language Processing}\cite{rothman2022transformers} by Denis Rothman, Antonio Gulli
+\end{itemize}
+\subsubsection{Related Work}
+\begin{itemize}
+	\item \textbf{Human-AI Collaboration Enables More Empathic Conversations in Text-based Peer-to-Peer Mental Health Support}\cite{sharma2022humanai}
+	\item \textbf{Context Matters: Recovering Human Semantic Structure from Machine Learning Analysis of Large-Scale Text Corpora}\cite{https://doi.org/10.1111/cogs.13085}
 \end{itemize}
@@
 The primary issue was the lack of these methods' ability to capture semantical and contextual aspects of our dataset.
+SVMs, DTs, LogReg, and RFs weren't built specifically for sequential data.
+For sequential data, RNNs and CNNs were classically used.
+However, due to the long-term dependency problem of RNNs, we made the decision to not use them, as we believed that they would not be able to capture the long-term dependencies in our dataset.
+Additionally, we weren't able to guarantee that during inference, there would be no long-term dependencies.
 Another issue was TF-IDF's lack of word order understanding.
@@
 \subsection{Short Intro on Transformers}
-The Transformer\cite{vaswani2017attention} is a deep learning model proposed in 2017 by a team of Google Brain researchers.
+The Transformer is a deep learning model proposed in 2017 by a team of Google Brain/Google Research researchers.
 It is mainly used in NLP, but it has also found its way into numerous vision projects (Latent Diffusion\cite{rombach2021highresolution}/Stable Diffusion/LLaVA\cite{liu2023visual}, to name a few).
@@
 To minimize error caused by input data, we removed all users with less than 25 messages, URLs, markdown code blocks, Discord mentions and custom emoji, and attachments.
-The resulting dataset was split into 85\% training, 10\% validation, and 5\% test sets.
+The resulting dataset was split into 75\% training, 10\% validation, and 15\% test sets.
 
@@
 \end{itemize}
+These features were selected based on what we thought would most accurately represent a user's text communication behavior.
+We projected that no two users would have the same or closely similar values for all of these features, which would allow us to differentiate between them.
 Then, we concatenate all the features into a single vector $e_u$ (of size $d_e$):

### 2023-05-18 acaris_ds.py

@@ -44,15 +44,12 @@ class ACARISDs(Dataset):
 		inputIDsPadded[:len(tokens["input_ids"].squeeze())] = tokens["input_ids"].squeeze()
 		attentionMaskPadded[:len(tokens["attention_mask"].squeeze())] = tokens["attention_mask"].squeeze()
 
-		userEmbedding = self.userEmbedder.get_user_embedding(userID)
-
 		print(f"input_ids shapes: {tokens['input_ids'].squeeze().shape}")
 		print(f"attention_mask shapes: {tokens['attention_mask'].squeeze().shape}")
-		print(f"userEmbedding shape: {userEmbedding.shape}")
 
 		return {
 			"input_ids": inputIDsPadded,
 			"attention_mask": attentionMaskPadded,
-			"userEmbedding": userEmbedding,
+			"userID": userID,
 			"labels": torch.tensor(label, dtype=torch.long)
 		}

### 2023-05-18 acaris_mdl.py

@@ -13,9 +13,10 @@ class ACARISMdl(nn.Module):
 		self.device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
 		self.to(self.device)
 
-	def forward(self, input_ids, attention_mask, userEmbedding, labels=None):
+	def forward(self, input_ids, attention_mask, userID, labels=None):
 		bertOut = self.bert(input_ids=input_ids, attention_mask=attention_mask)
 		tokenEmbs = bertOut.last_hidden_state[:, 0, :]
+		userEmbedding = self.userEmbedder.get_user_embedding(userID)
 		if userEmbedding is None:
 			userEmbedding = torch.zeros((input_ids.shape[0], 13), device=tokenEmbs.device)
 		userEmbs = userEmbedding.to(tokenEmbs.device)

### 2023-05-18 inferDistilBERT.py

@@ -1,0 +1,40 @@
+from transformers import DistilBertTokenizerFast
+import torch
+import sys
+from trainDistilBERT import DistilBertForMulticlassSequenceClassification
+import os
+import numpy as np
+import wandb
+
+wandb.init(mode="disabled")
+os.environ["WANDB_MODE"] = "disabled"
+
+class InferACARISBERT:
+	def __init__(self, mdlPath):
+		self.mdlPath = mdlPath
+		self.tokenizer = DistilBertTokenizerFast.from_pretrained("distilbert-base-uncased")
+		self.model = DistilBertForMulticlassSequenceClassification.from_pretrained(self.mdlPath)
+
+	def prepare_input(self, text):
+		inputs = self.tokenizer(text, truncation=True, padding="max_length", max_length=512, return_tensors="pt")
+		return inputs
+
+	def predict(self, inputs):
+		outputs = self.model(**inputs)
+		probs = torch.nn.functional.softmax(outputs.logits, dim=-1)
+		return probs.detach().cpu().numpy()
+
+	def infer(self):
+		for text in sys.stdin:
+			text = text.strip()
+			inputs = self.prepare_input(text)
+			pred = self.predict(inputs)
+			print(f"Input: {text}\nPrediction: {pred}\n")
+			maxProb = np.argmax(pred, axis=-1)
+			label = self.model.config.id2label[maxProb[0]]
+			confidence = pred[0][maxProb[0]]
+			print(f"Label: {label}\nConfidence: {confidence}\n")
+
+if __name__ == "__main__":
+	acaris_bert_infer = InferACARISBERT("./output")
+	acaris_bert_infer.infer()

### 2023-05-18 labelSent-3classes_ensemble.py

@@ -1,0 +1,96 @@
+from transformers import DistilBertTokenizer, DistilBertForSequenceClassification, pipeline
+from textblob import TextBlob
+from vaderSentiment.vaderSentiment import SentimentIntensityAnalyzer
+from flair.models import TextClassifier
+from flair.data import Sentence
+import pandas as pd
+from tqdm import tqdm
+import torch
+from collections import Counter
+import os
+
+maxLen = 512
+ckptFreq = 1000
+
+sourcePath = "./datasets/currentlyWorkingDataset/all_noTimestamps.csv"
+targetPath = "./datasets/currentlyWorkingDataset/all_noTimestamps_sent_ENSEMBLE.csv"
+
+source = pd.read_csv(sourcePath, sep="|", header=0)
+source["content"] = source["content"].astype(str)
+
+if os.path.exists(targetPath):
+	target = pd.read_csv(targetPath, sep="|", header=0)
+
+	assert all(target.iloc[:, :-1].eq(source.iloc[:target.shape[0], :-1]).all(axis=1)), "target and source datasets do not match"
+
+	index = target.shape[0]
+else:
+	target = source.copy()
+	target["sentiment"] = ""
+	target.to_csc(targetPath, sep="|", index=False)
+
+vader = SentimentIntensityAnalyzer()
+flair = TextClassifier.load("en-sentiment")
+
+tokenizer = DistilBertTokenizer.from_pretrained("distilbert-base-uncased")
+model = DistilBertForSequenceClassification.from_pretrained("distilbert-base-uncased-finetuned-sst-2-english")
+twitterRoberta = pipeline("sentiment-analysis", model="cardiffnlp/twitter-roberta-base-sentiment-latest", tokenizer="cardiffnlp/twitter-roberta-base-sentiment-latest")
+
+def get_sentiment(text):
+	# sanity conversion
+	text = str(text) # just in case
+
+	chunks = [text[i:i+maxLen] for i in range(0, len(text), maxLen)]
+	allSents = []
+
+	for chunk in chunks:
+
+		# DistilBERT
+		inputs = tokenizer(chunk, return_tensors="pt")
+		with torch.no_grad():
+			logits = model(**inputs).logits
+		probabilities = torch.nn.functional.softmax(logits, dim=-1)
+		prediction = probabilities.argmax().item()
[…]

### 2023-05-18 testDistilBERT.py

@@ -1,0 +1,72 @@
+import pandas as pd
+from transformers import DistilBertTokenizerFast, Trainer, TrainingArguments
+from datasets import Dataset
+import torch
+import wandb
+from sklearn.metrics import accuracy_score, precision_recall_fscore_support
+from trainDistilBERT import DistilBertForMulticlassSequenceClassification
+
+wandb.init(project="MarkIII_ACARIS", entity="simtoonia")
+
+
+
+class TestACARISBERT:
+	def __init__(self, mdlPath, testPath):
+		self.mdlPath = mdlPath
+		self.testPath = testPath
+		self.tokenizer = DistilBertTokenizerFast.from_pretrained("distilbert-base-uncased")
+		self.model = DistilBertForMulticlassSequenceClassification.from_pretrained(self.mdlPath)
+
+	def read_data(self, path):
+		df = pd.read_csv(path, sep="|", usecols=["content", "sentiment"])
+		return Dataset.from_pandas(df)
+
+	def tokenize_data(self, dataset):
+		sentMapping = {"pos": 2, "neg": 0, "neu": 1}
+		tokenized = dataset.map(
+			lambda x: {
+				**self.tokenizer(x["content"], truncation=True, padding="max_length", max_length=512),
+				"labels": torch.tensor([sentMapping[sent] for sent in x["sentiment"]])
+			},
+			batched=True,
+			remove_columns=["content", "sentiment"]
+		)
+		tokenized.set_format(type="torch", columns=["input_ids", "attention_mask", "labels"])
+		return tokenized
+
+	def compute_metrics(self, evalPred):
+		logits, labels = evalPred
+		preds = torch.argmax(torch.Tensor(logits), dim=1)
+		precision, recall, f1, _ = precision_recall_fscore_support(labels, preds, average=None)
+		metrics = {
+			"accuracy": accuracy_score(labels, preds)
+		}
+		metricNames = ["precision", "recall", "f1"]
+		labelNames = ["neg", "neu", "pos"]
+		for metricName, metricValue in zip(metricNames, [precision, recall, f1]):
+			for labelName, value in zip(labelNames, metricValue):
+				metrics[f"{metricName}_{labelName}"] = float(value)
+		return metrics
+
+	def test(self):
+		testDS = self.tokenize_data(self.read_data(self.testPath))
+
+		trainingArgs = TrainingArguments(
+			output_dir="./output",
[…]

### 2023-05-18 trainDistilBERT.py

@@ -5,27 +5,60 @@ This mod fine-tunes a BERT model on the ACARIS dataset for comparison with ACARI
 import torch
 from torch import nn
 from torch.utils.data import Dataset, DataLoader
-from transformers import DistilBertTokenizerFast, DistilBertForSequenceClassification, TrainingArguments, Trainer, AdamW, EarlyStoppingCallback
+from transformers import DistilBertTokenizerFast, DistilBertForSequenceClassification, TrainingArguments, Trainer, AdamW, EarlyStoppingCallback, PreTrainedModel, DistilBertModel
+from transformers.modeling_outputs import SequenceClassifierOutput
 from datasets import load_dataset, Dataset
 import pandas as pd
 from sklearn.metrics import accuracy_score, precision_recall_fscore_support
 import wandb
 import huggingface_hub
+import os
 
 config = {
 	"mdl": "distilbert-base-uncased",
-	"epochs": 5,
+	"epochs": 2,
 	"batchSize": 12,
     "maxLen": 512,
-    "warmupSteps": 750,
+    "warmupSteps": 0.1, # proportion of total steps, NOT absolute
     "weightDecay": 0.02,
 	"outputDir": "./output",
     "earlyStopping": True,
     "earlyStoppingPatience": 2,
-    "dropout": 0.1
+    "dropout": 0.1,
+    "lr": 5e-5,
+    "epsilon": 1e-8
 }
 
 wandb.init(project="MarkIII_ACARIS", entity="simtoonia", config=config)
+
+
+
+class DistilBertForMulticlassSequenceClassification(DistilBertForSequenceClassification):
+    def __init__(self, config):
+        super().__init__(config)
+
+    def forward(self, input_ids=None, attention_mask=None, head_mask=None, inputs_embeds=None, labels=None, output_attentions=None, output_hidden_states=None, return_dict=None):
+        return_dict = return_dict if return_dict is not None else self.config.use_return_dict
+
+        outputs = self.distilbert(input_ids, attention_mask=attention_mask, head_mask=head_mask, inputs_embeds=inputs_embeds, output_attentions=output_attentions, output_hidden_states=output_hidden_states, return_dict=return_dict)
+
+        hidden_state = outputs[0]
+        pooled_output = hidden_state[:, 0]
+        pooled_output = self.pre_classifier(pooled_output)
+        pooled_output = nn.ReLU()(pooled_output)
+        pooled_output = self.dropout(pooled_output)
[…]

### 2023-05-23 paper.tex
progress done, baseline models established, now working purely on ACARIS

@@
 	\item \textbf{Transformers for Natural Language Processing}\cite{rothman2022transformers} by Denis Rothman, Antonio Gulli
+	\item 
 \end{itemize}
@@
 \subsection{Short Intro on Transformers}
-The Transformer is a deep learning model proposed in 2017 by a team of Google Brain/Google Research researchers.
+The Transformer is a deep learning model architecture proposed in 2017 by a team of Google Brain/Google Research researchers.
 It is mainly used in NLP, but it has also found its way into numerous vision projects (Latent Diffusion\cite{rombach2021highresolution}/Stable Diffusion/LLaVA\cite{liu2023visual}, to name a few).
+The architecture aims to replace RNNs by using attentions mechanisms (self-attention, in particular) and positional encodings to model long-term dependencies in sequential data.
 
@@
 \section{Validation}
-To validate our approach, we compared the performance of our model with the performance of a baseline model.
+To validate our approach, we compared the performance of our model to the performance of a baseline model.
 We used the same model, DistilBERT, but without the user embeddings $e_u$.
 We fine-tuned both models on the same dataset and compared their performance on the same test set.
+The base model performed as follows (mean scores over 5 training runs):
+\begin{itemize} %%% (1/5)
+	\item \textbf{Accuracy} $\approx$ 0.95
+	\item \textbf{Precision\textsubscript{\textnormal{mean of all three scores}}} = 0.93
+	\item \textbf{Recall\textsubscript{\textnormal{mean of all three scores}}} = 0.93
+	\item \textbf{F1\textsubscript{\textnormal{mean of all three scores}}} $\approx$ 0.93
+\end{itemize}
+The model with user embeddings $e_u$ performed as follows (mean scores over 5 training runs):
+\begin{itemize}
+	\item \textbf{Accuracy} $\approx$ 0.97
+	\item \textbf{Precision\textsubscript{\textnormal{mean of all three scores}}} = NaN
+	\item \textbf{Recall\textsubscript{\textnormal{mean of all three scores}}} = NaN
+	\item \textbf{F1\textsubscript{\textnormal{mean of all three scores}}} $\approx$ NaN
+\end{itemize}
 \section{Results}

### 2023-05-23 acaris_collator.py

@@ -20,7 +20,7 @@ class ACARISCollator:
 				inputIDs[idx, len(feat["input_ids"]):] = torch.zeros(maxLen - len(feat["input_ids"]), dtype=torch.long)
 				attentionMask[idx, len(feat["attention_mask"]):] = torch.zeros(maxLen - len(feat["attention_mask"]), dtype=torch.long)
 
-		userEmbs = torch.stack([feat["userEmbedding"] for feat in feats])
+		userEmbs = torch.stack([self.userEmbedder.get_user_embedding(feat["userID"]) for feat in feats])
 		labels = torch.stack([feat["labels"] for feat in feats])
 
 		return {

### 2023-05-23 acaris_ds.py

@@ -9,9 +9,11 @@ class ACARISDs(Dataset):
 		self.data = data
 		self.preprocessor = preprocessor
 		self.userEmbedder = userEmbedder
-
+		print(self.data.head())
+		print(f"Number of samples before filtering: {len(self.data)}")
+		breakpoint()
 		self.data = self.data.iloc[1:] # remove zeroth row (header)
-		self.data = self.data[self.data["uid"].apply(lambda uid: self.userEmbedder.get_user_embedding(uid) is not None)]
+		self.data = self.data[self.data["uid"].apply(lambda uid: isinstance(self.userEmbedder.get_user_embedding(uid), torch.Tensor))] # filter out users with no userEmbedding
 		print(f"Number of samples after filtering: {len(self.data)}")
 
 		self.tokenized = [self.preprocessor.tokenize(text, padding=False, truncation=False, returnTensors=None) for text in self.data["content"]]

### 2023-05-23 acaris_trainer.py

@@ -2,8 +2,10 @@ from transformers import Trainer, TrainerCallback, EvalPrediction
 import torch.nn as nn
 import torch
 from tqdm.auto import tqdm
-from sklearn.metrics import accuracy_score, f1_score
-
+from sklearn.metrics import accuracy_score, f1_score, precision_recall_fscore_support, confusion_matrix, roc_auc_score, classification_report
+import wandb
+from wandb import AlertLevel
+from alert import send_alert
 
 
 class ProgressCb(TrainerCallback):
@@ -47,6 +49,7 @@ class ACARISTrainer(Trainer):
 		super().__init__(*args, **kwargs)
 		self.trainLoader = trainLoader
 		self.evalLoader = evalLoader
+		self.lossFct = ACARISCrossEntropyLoss(model.bert.config.num_labels)
 
 	def get_train_dataloader(self):
 		if self.trainLoader is not None:
@@ -86,26 +89,50 @@ class ACARISTrainer(Trainer):
 			print(f"labels.shape in compute_loss: {labels.shape}")
 			print(f"logits.shape in compute_loss: {logits.shape}")
 
-			lossFct = ACARISCrossEntropyLoss(model.bert.config.num_labels)
+			
 			labels = torch.clamp(labels, min=0, max=model.bert.config.num_labels - 1)
-			loss = lossFct(logits, labels)
+			loss = self.lossFct(logits, labels)
 		else:
 			raise ValueError("labels is None")
 
 		return (loss, outputs) if return_outputs else loss
 
+	# def compute_metrics(self, evalPred: EvalPrediction):
+	# 	logits, labels = evalPred.predictions, evalPred.label_ids
+	# 	predictions = torch.argmax(logits, dim=-1)
+
+	# 	if len(labels) > 0:
+	# 		acc = (predictions == labels).sum().item() / len(labels)
+	# 	else:
+	# 		acc = 0
+			
+	# 	wandb.log({"eval_accuracy": acc})
+	# 	metrics = {"eval_accuracy": acc}
+	# 	print(f"metrics: {metrics}")
+	# 	return metrics
+
 	def compute_metrics(self, evalPred: EvalPrediction):
 		logits, labels = evalPred.predictions, evalPred.label_ids
-		predictions = torch.argmax(logits, dim=-1)
-
+		logits = torch.softmax(torch.Tensor(logits), dim=1)
+		preds = torch.argmax(logits, dim=1)
 		if len(labels) > 0:
[…]

### 2023-05-23 alert.py

@@ -1,10 +1,25 @@
 import subprocess
+import requests
+import json
+from time import sleep
 
-def send_alert(title, message, urgency, time):
-	subprocess.run(["notify-send", "-u", urgency, "-t", str(time), title, message])
+def send_alert(title, message, urgency, time, sound=False, discord=False):
+	subprocess.run(["xset", "dpms", "force", "on"])
+	if discord:
+		data = {
+			"content": f"!!!!!!!!!! **{title}** !!!!!!!!!!\n{message}",
+			"username": "ACARISTrainer"
+		}
+
+		response = requests.post("https://discord.com/api/webhooks/1109919684050034719/E0Nz1r5qXAsRP_EJfAGaJmRPXS_fnJLg3tCsxpcjssZUBC2JWdTP-zpbD3o2tmQShFvy", json=data)
+	if sound: # beep using sound that lasts 8 second until killed
+		while True:
+			subprocess.run(["aplay", "-q", "/home/simtoon/Documents/alarm.wav"])
+			sleep(8)
+
 
 def emit_test_alert():
-	send_alert("Test", "This is a test alert", "critical", 5000)
+	send_alert("Test", "This is a test alert", "critical", 5000, sound=True, discord=True)
 
 if __name__ == "__main__":
 	emit_test_alert()

### 2023-05-23 data_loader.py

@@ -6,7 +6,8 @@ def load_data(dataType):
 		raise ValueError("dataType must be one of train, val, or test")
 
 	data = pd.read_csv(f"datasets/{dataType}.csv", sep="|")
-	data.columns = ["uid", "timestamp", "content", "sentiment"]
+#	data.columns = ["uid", "timestamp", "content", "sentiment"]
+	data.columns = ["uid", "content", "sentiment"]
 
 	if "neu" in data.columns:
 		data = data.rename(columns={"neu": "sentiment"})
@@ -58,4 +59,4 @@ def split_data(data, trainRatio, valRatio):
 
 if __name__ == "__main__":
 	#split_data("./datasets/sentAnal/sents_merged_cleaned.csv", 0.75, 0.1)
-	split_data("./datasets/all_noTimestamps.csv", 0.75, 0.1)
+	split_data("./datasets/currentlyWorkingDataset/all_noTimestamps_sent_ENSEMBLE.csv", 0.75, 0.1)

### 2023-05-23 feature_extract.py

@@ -18,7 +18,6 @@ import csv
 import argparse
 import os
 
-os.environ["TF_CPP_MIN_LOG_LEVEL"] = "2"
 
 emojiPattern = re.compile("["
 	u"\U0001F600-\U0001F64F" # facial emojis
@@ -56,7 +55,6 @@ class FeatExtractor:
 	def extract_feats(self, msgs, userID=None):
 		if not msgs:
 			return []
-		msgs = [msg for msg in msgs if len(msg["content"]) >= 25]
 		if not msgs:
 			return []
 
@@ -70,8 +68,8 @@ class FeatExtractor:
 			"meanPunctuationCount": self.mean_punctuation_count(msgs),
 			"meanSentimentScore": self.mean_sentiment_score(msgs),
 			"dominantTopics": self.dominant_topics(msgs),
-			"meanResponseTime": self.mean_response_time(msgs),
-			"meanMsgCountPerDay": self.mean_msg_count_per_day(msgs),
+			#"meanResponseTime": self.mean_response_time(msgs),
+			#"meanMsgCountPerDay": self.mean_msg_count_per_day(msgs),
 			"meanLinksPerMsg": self.mean_links_per_msg(msgs),
 			"meanCodeSnippetsPerMsg": self.mean_code_snippets_per_msg(msgs),
 			#"dominantWritingStyles": self.dominant_writing_styles(msgs),
@@ -88,14 +86,13 @@ class FeatExtractor:
 				raise ValueError
 		return feats if all(v is not None for v in feats.values()) else []
 
-	def save_feats_for_later(self, feats, path):
+	def save_feats_for_later(self, feats, userID, path):
 		with open(path, "wb") as f:
 			pickle.dump(feats, f)
 		
-		with open(path + ".csv", "w") as f:
+		with open(path + ".csv", "a") as f:
 			writer = csv.writer(f)
-			for feat in feats:
-				writer.writerow(feat)
+			writer.writerow([userID] + feats)
 
 	def load_feats(self, path):
 		with open(path, "rb") as f:
@@ -104,7 +101,8 @@ class FeatExtractor:
 
 	def read_msgs_from_file(self, path):
 		with open(path, "r", encoding="utf8") as f:
-			fieldNames = ["uid", "timestamp", "content", "sentiment"]
+			#fieldNames = ["uid", "timestamp", "content", "sentiment"]
+			fieldNames = ["uid", "content", "sentiment"]
 			reader = csv.DictReader(f, fieldnames=fieldNames, delimiter="|")
[…]

### 2023-05-23 inferDistilBERT.py

@@ -35,6 +35,11 @@ class InferACARISBERT:
 			confidence = pred[0][maxProb[0]]
 			print(f"Label: {label}\nConfidence: {confidence}\n")
 
+	def push(self, modelName, org="ongknsro"):
+		self.model.push_to_hub(repo_id=f"{org}/{modelName}", private=True)
+		self.tokenizer.push_to_hub(repo_id=f"{org}/{modelName}")
+
 if __name__ == "__main__":
 	acaris_bert_infer = InferACARISBERT("./output")
-	acaris_bert_infer.infer()
+	#acaris_bert_infer.infer()
+	acaris_bert_infer.push("ACARISBERT-DistilBERT")

### 2023-05-23 labelSent-3classes_ensemble.py

@@ -8,26 +8,44 @@ from tqdm import tqdm
 import torch
 from collections import Counter
 import os
+import transformers
+import string
+from alert import send_alert
 
-maxLen = 512
+maxLen = 510 # 512 - 2 because of special tokens
 ckptFreq = 1000
 
 sourcePath = "./datasets/currentlyWorkingDataset/all_noTimestamps.csv"
 targetPath = "./datasets/currentlyWorkingDataset/all_noTimestamps_sent_ENSEMBLE.csv"
 
 source = pd.read_csv(sourcePath, sep="|", header=0)
+source = source.dropna()
+source = source[source["content"].str.strip() != ""].reset_index(drop=True)
+source = source[source["content"].str.strip().apply(lambda x: any(c in string.printable for c in x))].reset_index(drop=True)
 source["content"] = source["content"].astype(str)
 
 if os.path.exists(targetPath):
-	target = pd.read_csv(targetPath, sep="|", header=0)
+	target = pd.read_csv(targetPath, sep="|", header=0, dtype={"sentiment": str})
+	target["content"] = target["content"].astype(str)
 
-	assert all(target.iloc[:, :-1].eq(source.iloc[:target.shape[0], :-1]).all(axis=1)), "target and source datasets do not match"
-
-	index = target.shape[0]
+	if not target.empty:
+		sharedCols = list(set(target.columns) & set(source.columns) - {"sentiment"})
+		nonmatching_rows = target[sharedCols].ne(source[sharedCols].iloc[:target.shape[0]]).any(axis=1)
+		if nonmatching_rows.any():
+			print("These rows do not match:")
+			print("In source:")
+			print(source.iloc[nonmatching_rows.values])
+			print("In target:")
+			print(target[nonmatching_rows])
+		assert all(target[sharedCols].eq(source[sharedCols].iloc[:target.shape[0], :]).all(axis=1)), "target and source datasets do not match"
+		index = target.shape[0]
+	else:
+		index = 0
 else:
 	target = source.copy()
 	target["sentiment"] = ""
-	target.to_csc(targetPath, sep="|", index=False)
+	target.to_csv(targetPath, sep="|", index=False)
+	index = 0
 
 vader = SentimentIntensityAnalyzer()
 flair = TextClassifier.load("en-sentiment")
[…]

### 2023-05-23 train.py

@@ -70,37 +70,6 @@ class MdlTrainer:
 		trainer.train()
 
 if __name__ == "__main__":
-
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
-	####### !!!!!!!!!!!! DO NOT TRAIN UNTIL DATA IS FIXED !!!!!!!!!!!! ########
[…]

### 2023-05-23 trainBERT.py

@@ -5,23 +5,27 @@ This mod fine-tunes a BERT model on the ACARIS dataset for comparison with ACARI
 import torch
 from torch import nn
 from torch.utils.data import Dataset, DataLoader
-from transformers import BertTokenizerFast, BertForSequenceClassification, TrainingArguments, Trainer, AdamW, EarlyStoppingCallback
+from transformers import BertTokenizerFast, BertForSequenceClassification, TrainingArguments, Trainer, AdamW, EarlyStoppingCallback, PreTrainedModel, BertModel
+from transformers.modeling_outputs import SequenceClassifierOutput
 from datasets import load_dataset, Dataset
 import pandas as pd
 from sklearn.metrics import accuracy_score, precision_recall_fscore_support
 import wandb
+import huggingface_hub
+import os
 
 config = {
 	"mdl": "bert-base-uncased",
-	"epochs": 1,
-	"batchSize": 12,
+	"epochs": 5,
+	"batchSize": 14,
     "maxLen": 512,
-    "warmupSteps": 500,
-    "weightDecay": 0.01,
+    "warmupSteps": 0.1, # proportion of total steps, NOT absolute
+    "weightDecay": 0.02,
 	"outputDir": "./output",
     "earlyStopping": True,
     "earlyStoppingPatience": 2,
-    "dropout": 0.1
+    "initlr": 5e-5,
+    "epsilon": 1e-8
 }
 
 wandb.init(project="MarkIII_ACARIS", entity="simtoonia", config=config)
@@ -33,8 +37,10 @@ class ACARISBERT:
         self.trainPath = trainPath
         self.valPath = valPath
         self.tokenizer = BertTokenizerFast.from_pretrained(config["mdl"])
-        self.model = BertForSequenceClassification.from_pretrained(config["mdl"], num_labels=3)
-        
+        self.model = BertForSequenceClassification.from_pretrained(config["mdl"], num_labels=3, id2label={0: "neg", 1: "neu", 2: "pos"}, label2id={"neg": 0, "neu": 1, "pos": 2})
+
+
+
     def read_data(self, path):
         df = pd.read_csv(path, sep="|", usecols=["content", "sentiment"])
         return Dataset.from_pandas(df)
@@ -53,7 +59,7 @@ class ACARISBERT:
         return tokenized
     
     def get_data_loaders(self, trainDS, valDS):
-        trainLoader = DataLoader(trainDS, batch_size=config["batchSize"], shuffle=True)
[…]

### 2023-05-23 trainDistilBERT.py

@@ -9,15 +9,17 @@ from transformers import DistilBertTokenizerFast, DistilBertForSequenceClassific
 from transformers.modeling_outputs import SequenceClassifierOutput
 from datasets import load_dataset, Dataset
 import pandas as pd
-from sklearn.metrics import accuracy_score, precision_recall_fscore_support
+from sklearn.metrics import accuracy_score, precision_recall_fscore_support, confusion_matrix, roc_auc_score
 import wandb
 import huggingface_hub
 import os
+import random
+import numpy as np
 
 config = {
 	"mdl": "distilbert-base-uncased",
-	"epochs": 2,
-	"batchSize": 12,
+	"epochs": 5,
+	"batchSize": 14,
     "maxLen": 512,
     "warmupSteps": 0.1, # proportion of total steps, NOT absolute
     "weightDecay": 0.02,
@@ -25,13 +27,23 @@ config = {
     "earlyStopping": True,
     "earlyStoppingPatience": 2,
     "dropout": 0.1,
-    "lr": 5e-5,
+    "initlr": 5e-5,
     "epsilon": 1e-8
 }
 
 wandb.init(project="MarkIII_ACARIS", entity="simtoonia", config=config)
 
 
+def lockSeed(seed):
+    random.seed(seed)
+    np.random.seed(seed)
+    torch.manual_seed(seed)
+    if torch.cuda.is_available():
+        torch.cuda.manual_seed_all(seed)
+        torch.backends.cudnn.deterministic = True
+
+#0 disabled, as determinism is not guaranteed and lowers performance
+#lockSeed(69) # setting a fixed seed for *some* reproducibility
 
 class DistilBertForMulticlassSequenceClassification(DistilBertForSequenceClassification):
     def __init__(self, config):
@@ -89,7 +101,7 @@ class ACARISBERT:
         return tokenized
     
     def get_data_loaders(self, trainDS, valDS):
-        trainLoader = DataLoader(trainDS, batch_size=config["batchSize"], shuffle=True)
+        trainLoader = DataLoader(trainDS, batch_size=config["batchSize"], shuffle=False)
         valLoader = DataLoader(valDS, batch_size=config["batchSize"], shuffle=False)
         return trainLoader, valLoader
     
@@ -97,8 +109,13 @@ class ACARISBERT:
         logits, labels = evalPred
         preds = torch.argmax(torch.Tensor(logits), dim=1)
         precision, recall, f1, _ = precision_recall_fscore_support(labels, preds, average=None)
[…]

### 2023-05-23 trainRoBERTa.py

@@ -1,5 +1,5 @@
 """
-This mod fine-tunes a BERT model on the ACARIS dataset for comparison with ACARISMdl.
+This mod fine-tunes a RoBERTa model on the ACARIS dataset for comparison with ACARISMdl.
 """
 
 import torch
@@ -105,7 +105,7 @@ class ACARISBERT:
             compute_metrics=self.compute_metrics,
             callbacks=[EarlyStoppingCallback(early_stopping_patience=config["earlyStoppingPatience"])]
         )
-        
+        trainer.evaluate()
         trainer.train()
         trainer.save_model(config["outputDir"])
         
@@ -113,5 +113,5 @@ class ACARISBERT:
 if __name__ == "__main__":
     acaris_bert = ACARISBERT("./datasets/train.csv", "./datasets/val.csv")
     acaris_bert.train()
-    acaris_bert.push_to_hub()
+    #acaris_bert.push_to_hub()
     wandb.finish()

### 2023-05-23 user_embedder.py

@@ -7,37 +7,46 @@ from feature_extract import FeatExtractor
 
 
 class UserEmbedder:
-    def __init__(self, userEmbeddingSize=10):
-        self.mdl = "distilbert-base-uncased"
-        self.userEmbeddings = {}
-        self.userEmbeddingSize = userEmbeddingSize
-        self.extractor = FeatExtractor(self.mdl)
-        self.msgs = self.extractor.read_msgs_from_file("./datasets/sentAnal/sents_merged_cleaned.csv")
+	def __init__(self, userEmbeddingSize=11):
+		self.mdl = "distilbert-base-uncased"
+		self.userEmbeddings = {}
+		self.userEmbeddingSize = userEmbeddingSize
+		self.extractor = FeatExtractor(self.mdl)
+		self.msgs = self.extractor.read_msgs_from_file("./datasets/currentlyWorkingDataset/all_noTimestamps_sent_ENSEMBLE.csv")
 
-    def get_user_embedding(self, userID):
-        if userID not in self.userEmbeddings:
-            feats = self.extractor.extract_and_store_feats(self.msgs, userID)
-            if feats is not None:
-                self.userEmbeddings[userID] = self.create_user_embedding(feats)
-            else:
-                #self.userEmbeddings[userID] = torch.zeros(13, dtype=torch.float)
-                self.userEmbeddings[userID] = None
-        return self.userEmbeddings[userID]
+		#0 format of self.msgs is a list of dicts, each dict equal to a row in the csv (i.e. a message) (i.e. a dict of the format {"userID": userID, "content": content, "sentiment": sentiment})
+	# BUG: self.msgs is empty, so no user embeddings are created
+	def get_user_embedding(self, userID):
+		if userID not in self.userEmbeddings:
+			print(f"Creating user embedding for user {userID}")
+			print(f"self.msgs: {self.msgs}")
+			self.msgs = [msg for msg in self.msgs if msg["uid"] == userID]
+			self.msgs = [msg for msg in self.msgs if len(msg["content"]) >= 25] 
+			print(f"self.msgs: {self.msgs}")
+			breakpoint()
+			# filter out messages with less than 25 characters
+			feats = self.extractor.extract_and_store_feats(self.msgs, userID)
+			if feats is not None:
+				self.userEmbeddings[userID] = self.create_user_embedding(feats)
+			else:
+				print(f"Skipping user {userID} due to None feats")
+				return None
+		return self.userEmbeddings[userID]
 
[…]

### 2023-05-28 acaris_collator.py
Made some progress, almost made ACARIS work. good job, me ... LOL

@@ -3,10 +3,26 @@ import torch
 
 
 class ACARISCollator:
-	def __init__(self, device):
+	def __init__(self, device, userEmbedder):
 		self.device = device
+		self.userEmbedder = userEmbedder
 
 	def __call__(self, feats: List[Dict[str, torch.Tensor]]) -> Dict[str, torch.Tensor]:
+		"""
+		This function takes in a list of feature dictionaries, pads the input_ids and attention_mask tensors
+		to the maximum length, stacks the labels tensor, and returns a dictionary containing the padded
+		input_ids and attention_mask tensors, uids, and stacked labels tensor.
+		
+		@param feats A list of dictionaries, where each dictionary contains the input_ids, attention_mask,
+		uids, and labels for a single example in a dataset.
+		
+		@return a dictionary containing the following keys and their corresponding values:
+		- "input_ids": a tensor of shape (batch_size, maxLen) containing the input IDs of the input
+		sequences
+		- "attention_mask": a tensor of shape (batch_size, maxLen) containing the attention masks of the
+		input sequences
+		- "uids": a list of unique user identifiers for each input sequence
+		"""
 		maxLen = max([len(feat["input_ids"]) for feat in feats])
 
 		inputIDs = torch.zeros((len(feats), maxLen), dtype=torch.long)
@@ -20,12 +36,12 @@ class ACARISCollator:
 				inputIDs[idx, len(feat["input_ids"]):] = torch.zeros(maxLen - len(feat["input_ids"]), dtype=torch.long)
 				attentionMask[idx, len(feat["attention_mask"]):] = torch.zeros(maxLen - len(feat["attention_mask"]), dtype=torch.long)
 
-		userEmbs = torch.stack([self.userEmbedder.get_user_embedding(feat["userID"]) for feat in feats])
+		uids = [feat["uids"] for feat in feats]
 		labels = torch.stack([feat["labels"] for feat in feats])
 
 		return {
 			"input_ids": inputIDs,
 			"attention_mask": attentionMask,
-			"userEmbedding": userEmbs,
+			"uids": uids,
 			"labels": labels
 		}

### 2023-05-28 acaris_ds.py

@@ -2,6 +2,7 @@ from torch.utils.data import Dataset
 import torch
 from preprocess import Preprocessor
 from user_embedder import UserEmbedder
+from tqdm import tqdm
 
 
 class ACARISDs(Dataset):
@@ -9,20 +10,24 @@ class ACARISDs(Dataset):
 		self.data = data
 		self.preprocessor = preprocessor
 		self.userEmbedder = userEmbedder
-		print(self.data.head())
-		print(f"Number of samples before filtering: {len(self.data)}")
-		breakpoint()
 		self.data = self.data.iloc[1:] # remove zeroth row (header)
 		self.data = self.data[self.data["uid"].apply(lambda uid: isinstance(self.userEmbedder.get_user_embedding(uid), torch.Tensor))] # filter out users with no userEmbedding
-		print(f"Number of samples after filtering: {len(self.data)}")
 
-		self.tokenized = [self.preprocessor.tokenize(text, padding=False, truncation=False, returnTensors=None) for text in self.data["content"]]
 		self.maxLen = 512
 
-	def __len__(self):
+	def __len__(self) -> int:
 		return len(self.data)
 
-	def __getitem__(self, idx: int):
+	def __getitem__(self, idx: int) -> dict:
+		"""
+		This function returns a dictionary containing tokenized input, attention mask, unique IDs, and
+		labels for a given index in a dataset.
+		
+		@param idx idx is an integer representing the index of the sample to retrieve from the dataset.
+		
+		@return A dictionary containing the input IDs, attention mask, unique IDs, and labels of a sample
+		from the dataset.
+		"""
 		sentMapping = {"pos": 2, "neg": 0, "neu": 1} # adjusted due to CrossEntropyLoss
 		try:
 			if idx < 0 or idx >= len(self.data):
@@ -33,12 +38,12 @@ class ACARISDs(Dataset):
 		content = sample["content"]
 		label = sentMapping[sample["sentiment"]]
 		try:
-			userID = sample["uid"]
-		except KeyError:
-			print(f"KeyError at index {idx} with text {content} and label {label}")
+			uids = sample["uid"]
+		except Exception as e:
+			print(sample)
 			raise
 
-		tokens = self.preprocessor.tokenize(content)
[…]

### 2023-05-28 acaris_mdl.py

@@ -2,32 +2,50 @@ import torch
 import torch.nn as nn
 from transformers import AutoModel
 from user_embedder import UserEmbedder
+from acaris_trainer import ACARISCrossEntropyLoss
 
 
 class ACARISMdl(nn.Module):
 	def __init__(self, mdl, userEmbedder, numLabels = 3):
 		super().__init__()
 		self.bert = AutoModel.from_pretrained(mdl)
-		self.classifier = nn.Linear(self.bert.config.hidden_size + 13, numLabels)
+		self.classifier = nn.Linear(self.bert.config.hidden_size + 11, numLabels)
 		self.userEmbedder = userEmbedder
 		self.device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
+		self.lossFct = ACARISCrossEntropyLoss(self.bert.config.num_labels)
 		self.to(self.device)
 
-	def forward(self, input_ids, attention_mask, userID, labels=None):
+	def forward(self, input_ids, attention_mask, uids, labels=None):
+		"""
+		This function takes input_ids, attention_mask, and uids as inputs, and returns logits after
+		concatenating token and user embeddings.
+		
+		@param input_ids The input sequence of token ids for the BERT model.
+		@param attention_mask The attention mask is a binary tensor indicating which tokens in the input
+		sequence are padding tokens and which are not. Padding tokens are usually added to ensure that all
+		sequences in a batch have the same length. The attention mask is used by the transformer model to
+		ignore the padding tokens during computation.
+		@param uids The `uids` parameter is a list of user ids corresponding to the input sequence. It is
+		used to retrieve user embeddings from a user embedding matrix using a user embedding module
+		(`self.userEmbedder`). These user embeddings are then concatenated with the token embeddings
+		obtained from the BERT model to form the final input
+		@param labels The ground truth labels for the input data. If provided, the function will calculate
+		and return the loss along with the logits. If not provided, only the logits will be returned.
+		
+		@return If `labels` is not None, a dictionary with keys "loss" and "logits" is returned, where
+		"loss" is the calculated loss and "logits" are the predicted logits. If `labels` is None, a
+		dictionary with only the "logits" key is returned, containing only the predicted logits.
+		"""
[…]

### 2023-05-28 acaris_trainer.py

@@ -36,64 +36,81 @@ class ACARISCrossEntropyLoss(nn.Module):
 
 	def forward(self, logits, labels):
 		mapped = (labels + 1) // 2
-		print(f"mapped labels: {mapped}")
-		print(f"mapped labels.shape: {mapped.shape}")
-		print(f"original labels: {labels}")
-		print(f"original labels.shape: {labels.shape}")
 		return self.loss(logits, mapped)
 
 
 
 class ACARISTrainer(Trainer):
-	def __init__(self, trainLoader, evalLoader, progressCb=None, *args, **kwargs):
-		super().__init__(*args, **kwargs)
+	def __init__(self, model, trainLoader, evalLoader, progressCb=None, *args, **kwargs):
+		super().__init__(model=model, *args, **kwargs)
 		self.trainLoader = trainLoader
 		self.evalLoader = evalLoader
 		self.lossFct = ACARISCrossEntropyLoss(model.bert.config.num_labels)
 
 	def get_train_dataloader(self):
+		"""
+		This function returns the training data loader if it exists, otherwise it calls the parent class's
+		function to get the training data loader.
+		
+		@return If `self.trainLoader` is not `None`, then `self.trainLoader` is returned. Otherwise, the
+		method `get_train_dataloader()` of the parent class is called and its output is returned.
+		"""
 		if self.trainLoader is not None:
 			return self.trainLoader
 		else:
 			return super().get_train_dataloader()
 
 	def get_eval_dataloader(self, *args, **kwargs):
+		"""
+		This function returns the evaluation dataloader if it exists, otherwise it calls the parent class's
+		get_eval_dataloader method.
+		
+		@return If `self.evalLoader` is not `None`, then it returns `self.evalLoader`. Otherwise, it calls
+		the `get_eval_dataloader` method of the parent class (using `super()`) and returns its output.
+		"""
 		if self.evalLoader is not None:
 			return self.evalLoader
 		else:
 			return super().get_eval_dataloader(*args, **kwargs)
 
 	def train(self):
+		"""
+		The `train` function is called on the parent class using `super()` in a subclass.
+		"""
 		super().train()
 
 
-	def compute_loss(self, model, inputs, labels=None, return_outputs=False):
-		labels = inputs.pop("labels", None)
-		userEmbedding = inputs.pop("userEmbedding", None)
-		if userEmbedding is None or labels is None:
-			return (None, None) if return_outputs else None
[…]

### 2023-05-28 alert.py

@@ -5,6 +5,7 @@ from time import sleep
 
 def send_alert(title, message, urgency, time, sound=False, discord=False):
 	subprocess.run(["xset", "dpms", "force", "on"])
+	subprocess.run(["notify-send", "-u", urgency, "-t", str(time), title, message]) # possible urgency values for notify-send: low, normal, critical
 	if discord:
 		data = {
 			"content": f"!!!!!!!!!! **{title}** !!!!!!!!!!\n{message}",

### 2023-05-28 data_loader.py

@@ -1,5 +1,6 @@
 import pandas as pd
 from sklearn.model_selection import train_test_split
+from tqdm import tqdm
 
 def load_data(dataType):
 	if dataType not in ["train", "val", "test"]:
@@ -20,11 +21,18 @@ def load_data(dataType):
 
 	print(f"n of rows with pos sentiment: {len(data[data['sentiment'] == 'pos'])}")
 
+	for i in tqdm(range(len(data)), desc=f"Loading {dataType} data"):
+		pass
+
 	return data
 
-def split_data(data, trainRatio, valRatio):
+def split_data(data, trainRatio, valRatio, filterInsufficient):
 	data = pd.read_csv(data, sep="|")
 	data = data.loc[:, ~data.columns.str.startswith("Unnamed")]
+
+	if filterInsufficient:
+		data = data[data["content"].str.len() >= 25]
+		data = data.groupby("uid").filter(lambda x: len(x) >= 25)
 
 	dropped = 0
 
@@ -43,15 +51,21 @@ def split_data(data, trainRatio, valRatio):
 
 	testRatio = 1 - (trainRatio + valRatio)
 
-	trainData, tempData = train_test_split(data, train_size=trainRatio, random_state=69)
+	with tqdm(total=3, desc="Splitting data") as pbar:
 
-	adjValRatio = valRatio / testRatio
+		trainData, tempData = train_test_split(data, train_size=trainRatio, random_state=69)
+		pbar.update()
 
-	valData, testData = train_test_split(tempData, train_size=adjValRatio, random_state=69)
+		adjValRatio = valRatio / testRatio
 
-	trainData.to_csv("datasets/train.csv", index=False, sep="|")
-	valData.to_csv("datasets/val.csv", index=False, sep="|")
-	testData.to_csv("datasets/test.csv", index=False, sep="|")
+		valData, testData = train_test_split(tempData, train_size=adjValRatio, random_state=69)
+		pbar.update()
+
+		trainData.to_csv("datasets/train.csv", index=False, sep="|")
+		valData.to_csv("datasets/val.csv", index=False, sep="|")
+		testData.to_csv("datasets/test.csv", index=False, sep="|")
+
+		pbar.update()
 
 	print(f"Train columns: {trainData.columns}")
 
@@ -59,4 +73,4 @@ def split_data(data, trainRatio, valRatio):
 
 if __name__ == "__main__":
[…]

### 2023-05-28 feature_extract.py

@@ -209,13 +209,11 @@ class FeatExtractor:
 		groupedMsgs = self.group_msgs_by_user(msgs)
 
 		if userID is not None:
-			print(f"msgs: {msgs}")
-			breakpoint()
 			#if userID not in groupedMsgs or len(groupedMsgs[userID]) < 25:
 			if len(msgs) < 25:
-				print(f"Skipping {userID} because they have less than 25 messages")
 				return None
 			#msgs = groupedMsgs[userID] # disabled for now
+			assert all(msg["uid"] == userID for msg in msgs), f"msgs contains messages from multiple users: {[msg['uid'] for msg in msgs]}" #sanity check to ensure that all dicts in msgs belong to the same user
 			feats = self.extract_feats(msgs=msgs, userID=userID)
 			if not feats:
 				print(f"{userID} has 0 feats!")

### 2023-05-28 labelSent-3classes_ensemble.py

@@ -55,26 +55,6 @@ model = DistilBertForSequenceClassification.from_pretrained("distilbert-base-unc
 twitterRoberta = pipeline("sentiment-analysis", model="cardiffnlp/twitter-roberta-base-sentiment-latest", tokenizer="cardiffnlp/twitter-roberta-base-sentiment-latest")
 twitterRobertaTokenizer = transformers.AutoTokenizer.from_pretrained("cardiffnlp/twitter-roberta-base-sentiment-latest")
 
-# def get_chunks(text, tokenizer, maxLen):
-# 	words = text.split()
-# 	chunks = []
-# 	currentChunk = []
-# 	for word in words:
-# 		if len(tokenizer.encode(" ".join(currentChunk + [word]))) > maxLen:
-# 			chunks.append(" ".join(currentChunk))
-# 			currentChunk = [word]
-# 		else:
-# 			currentChunk.append(word)
-# 	if len(tokenizer.encode(" ".join(currentChunk))) > maxLen:
-# 		for word in currentChunk:
-# 			if len(tokenizer.encode(word)) > maxLen:
-# 				print(f"Word {word} is longer than maxLen {maxLen}, skipping")
-# 			else:
-# 				chunks.append(word)
-# 	else:
-# 		chunks.append(" ".join(currentChunk))
-# 	return chunks
-
 def get_sentiment(text):
 	try:
 		# sanity conversion

### 2023-05-28 train.py

@@ -16,6 +16,7 @@ from data_loader import load_data
 import os
 import wandb
 from acaris_trainer import ProgressCb
+from alert import send_alert
 
 os.environ["TOKENIZERS_PARALLELISM"] = "false"
 #os.environ["CUDA_LAUNCH_BLOCKING"] = "1"
@@ -35,14 +36,31 @@ class MdlTrainer:
 	def __init__(self, mdl, userEmbedder):
 		self.model = ACARISMdl(mdl, userEmbedder)
 		self.device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
-		#self.device = torch.device("cpu") # TODO: #1 fuck me, not enough VRAM. fuck me hard. ffs
-		self.model.to(self.device)
 		wandb.watch(self.model, log="all")
 
 	def fine_tune(self, trainLoader, valLoader, epochs, batchSize, outputDir):
+		"""
+		This function fine-tunes a given model using the provided training and validation data loaders, for
+		a specified number of epochs and batch size, and saves the output in a specified directory.
+		
+		@param trainLoader A DataLoader object containing the training data.
+		@param valLoader valLoader is a DataLoader object that contains the validation dataset. It is used
+		during the fine-tuning process to evaluate the performance of the model on a separate set of data
+		that it has not seen during training. This helps to prevent overfitting and ensures that the model
+		generalizes well to new data
+		@param epochs The number of times the model will iterate over the entire training dataset during
+		training.
+		@param batchSize The number of samples in a batch during training and evaluation.
+		@param outputDir The directory where the fine-tuned model will be saved.
+		"""
+		# Define a callback function for reporting progress
 		progressCb = ProgressCb()
+
+		# Create output directory if it doesn't exist
 		if not os.path.exists(outputDir):
 			os.makedirs(outputDir)
+
+		# Define training arguments
 		trainingArgs = TrainingArguments(  
 			output_dir=outputDir,
 			num_train_epochs=epochs,
@@ -63,18 +81,29 @@ class MdlTrainer:
 			args=trainingArgs,
 			trainLoader=trainLoader,
 			evalLoader=valLoader,
-			compute_metrics=ACARISTrainer.compute_metrics,
 			callbacks=[ProgressCb()]
 		)
-
[…]

### 2023-05-28 user_embedder.py

@@ -3,50 +3,96 @@ This mod handles user embeddings.
 """
 
 import torch
+import os
+from tqdm import tqdm
 from feature_extract import FeatExtractor
 
-
 class UserEmbedder:
-	def __init__(self, userEmbeddingSize=11):
+	def __init__(self, userEmbeddingSize) -> None:
 		self.mdl = "distilbert-base-uncased"
 		self.userEmbeddings = {}
 		self.userEmbeddingSize = userEmbeddingSize
 		self.extractor = FeatExtractor(self.mdl)
 		self.msgs = self.extractor.read_msgs_from_file("./datasets/currentlyWorkingDataset/all_noTimestamps_sent_ENSEMBLE.csv")
 
-		#0 format of self.msgs is a list of dicts, each dict equal to a row in the csv (i.e. a message) (i.e. a dict of the format {"userID": userID, "content": content, "sentiment": sentiment})
-	# BUG: self.msgs is empty, so no user embeddings are created
-	def get_user_embedding(self, userID):
-		if userID not in self.userEmbeddings:
-			print(f"Creating user embedding for user {userID}")
-			print(f"self.msgs: {self.msgs}")
-			self.msgs = [msg for msg in self.msgs if msg["uid"] == userID]
-			self.msgs = [msg for msg in self.msgs if len(msg["content"]) >= 25] 
-			print(f"self.msgs: {self.msgs}")
-			breakpoint()
-			# filter out messages with less than 25 characters
-			feats = self.extractor.extract_and_store_feats(self.msgs, userID)
-			if feats is not None:
-				self.userEmbeddings[userID] = self.create_user_embedding(feats)
-			else:
-				print(f"Skipping user {userID} due to None feats")
-				return None
-		return self.userEmbeddings[userID]
+		#0 format of self.msgs is a list of dicts, each dict equal to a row in the csv (i.e. a message) (i.e. a dict of the format {"uid": uid, "content": content, "sentiment": sentiment})
 
-	def update_user_embedding(self, userID):
-		feats = self.extractor.extract_and_store_feats(self.msgs, userID)
-		self.userEmbeddings[userID] = self.create_user_embedding(feats)
+	def get_user_embedding(self, uid) -> torch.Tensor:
+		"""
+		This function retrieves or creates a user embedding tensor based on the user's messages.
+		
+		@param uid uid stands for "user ID", which is a unique identifier assigned to each user in a system
+		or application. In this code, it is used to retrieve or create an embedding (a numerical
+		representation) for a specific user based on their messages.
+		
[…]

### 2023-05-28 train.py
Prepared the ACARIS train script for the big boy GPUs LOL (batchsize, epoch count, fp16=False)

@@ -23,8 +23,8 @@ os.environ["TOKENIZERS_PARALLELISM"] = "false"
 
 config = {
 	"mdl": "distilbert-base-uncased",
-	"epochs": 1,
-	"batchSize": 12,
+	"epochs": 5,
+	"batchSize": 32,
 	"outputDir": "./output"
 }
 
@@ -70,7 +70,7 @@ class MdlTrainer:
 			eval_steps=500,
 			save_strategy="steps",
 			save_steps=1000,
-			fp16=True,
+			fp16=False,
 			logging_dir="./logs",
 			load_best_model_at_end=True,
 			metric_for_best_model="eval_accuracy"

### 2023-05-30 alert.py
remove alert.py deps on graphical

@@ -4,8 +4,12 @@ import json
 from time import sleep
 
 def send_alert(title, message, urgency, time, sound=False, discord=False):
-	subprocess.run(["xset", "dpms", "force", "on"])
-	subprocess.run(["notify-send", "-u", urgency, "-t", str(time), title, message]) # possible urgency values for notify-send: low, normal, critical
+	try:
+		subprocess.run(["xset", "dpms", "force", "on"])
+		subprocess.run(["notify-send", "-u", urgency, "-t", str(time), title, message]) # possible urgency values for notify-send: low, normal, critical
+	except Exception as e:
+		print(f"Failed to send alert: {e}")
+		pass
 	if discord:
 		data = {
 			"content": f"!!!!!!!!!! **{title}** !!!!!!!!!!\n{message}",

### 2023-05-30 feature_extract.py

@@ -112,7 +112,6 @@ class FeatExtractor:
 			msgs = [row for row in reader if any(row.values())]
 			for msg in msgs:
 				msg.pop(None, None)
-				print(msg)
 		# return format: [{"uid": "user#1234", "content": "hello world", "sentiment": "pos"}, ...]
 		return msgs
 

### 2023-05-30 train.py
added hostname to the alerts when starting eval/training

@@ -17,6 +17,7 @@ import os
 import wandb
 from acaris_trainer import ProgressCb
 from alert import send_alert
+import socket
 
 os.environ["TOKENIZERS_PARALLELISM"] = "false"
 #os.environ["CUDA_LAUNCH_BLOCKING"] = "1"
@@ -84,14 +85,14 @@ class MdlTrainer:
 			callbacks=[ProgressCb()]
 		)
 		try:
-			send_alert("**WE ARE EVALUATING**", "Eval started", "low", 5000, sound=False, discord=True)
+			send_alert("**WE ARE EVALUATING**", f"Eval started on {socket.gethostname()}", "low", 5000, sound=False, discord=True)
 			trainer.evaluate()
 			send_alert("**EVALUATION COMPLETE**", "Eval complete", "low", 5000, sound=False, discord=True)
 		except Exception as e:
 			send_alert("!! EVAL FAILED !!", str(e), "critical", 50000, sound=True, discord=True)
 			raise
 		try:
-			send_alert("**WE ARE TRAINING**", "Training started", "low", 5000, sound=False, discord=True)
+			send_alert("**WE ARE TRAINING**", f"Training started on {socket.gethostname()}", "low", 5000, sound=False, discord=True)
 			trainer.train()
 			send_alert("**TRAINING COMPLETE**", "Training complete", "low", 5000, sound=False, discord=True)
 		except Exception as e:

### 2023-05-30 acaris_trainer.py
debugging the compute_metrics method ... stand by

@@ -163,6 +163,7 @@ class ACARISTrainer(Trainer):
 		for metricName, metricValue in zip(metricNames, [precision, recall, f1]):
 			for labelName, value in zip(labelNames, metricValue):
 				metrics[f"{metricName}_{labelName}"] = float(value)
+		print(f"metrics: {metrics}")
 		return metrics
 
 	def prediction_step(self, mdl, inputs: dict[str, torch.Tensor], prediction_loss_only, ignore_keys=None):

### 2023-05-30 alert.py

@@ -8,7 +8,7 @@ def send_alert(title, message, urgency, time, sound=False, discord=False):
 		subprocess.run(["xset", "dpms", "force", "on"])
 		subprocess.run(["notify-send", "-u", urgency, "-t", str(time), title, message]) # possible urgency values for notify-send: low, normal, critical
 	except Exception as e:
-		print(f"Failed to send alert: {e}")
+		print(f"Failed to send alert as notif: {e}")
 		pass
 	if discord:
 		data = {
@@ -19,7 +19,11 @@ def send_alert(title, message, urgency, time, sound=False, discord=False):
 		response = requests.post("https://discord.com/api/webhooks/1109919684050034719/E0Nz1r5qXAsRP_EJfAGaJmRPXS_fnJLg3tCsxpcjssZUBC2JWdTP-zpbD3o2tmQShFvy", json=data)
 	if sound: # beep using sound that lasts 8 second until killed
 		while True:
-			subprocess.run(["aplay", "-q", "/home/simtoon/Documents/alarm.wav"])
+			try:
+				subprocess.run(["aplay", "-q", "/home/simtoon/Documents/alarm.wav"])
+			except Exception as e:
+				print(f"Failed to play sound: {e}")
+				pass
 			sleep(8)
 
 

### 2023-05-30 train.py
adjusted alert

@@ -85,14 +85,14 @@ class MdlTrainer:
 			callbacks=[ProgressCb()]
 		)
 		try:
-			send_alert("**WE ARE EVALUATING**", f"Eval started on {socket.gethostname()}", "low", 5000, sound=False, discord=True)
+			send_alert("**WE ARE EVALUATING**", f"Eval started on `{socket.gethostname()}`", "low", 5000, sound=False, discord=True)
 			trainer.evaluate()
 			send_alert("**EVALUATION COMPLETE**", "Eval complete", "low", 5000, sound=False, discord=True)
 		except Exception as e:
 			send_alert("!! EVAL FAILED !!", str(e), "critical", 50000, sound=True, discord=True)
 			raise
 		try:
-			send_alert("**WE ARE TRAINING**", f"Training started on {socket.gethostname()}", "low", 5000, sound=False, discord=True)
+			send_alert("**WE ARE TRAINING**", f"Training started on `{socket.gethostname()}`", "low", 5000, sound=False, discord=True)
 			trainer.train()
 			send_alert("**TRAINING COMPLETE**", "Training complete", "low", 5000, sound=False, discord=True)
 		except Exception as e:

### 2023-05-30 acaris_trainer.py
moved the compute_metrics method to the main script

@@ -128,44 +128,6 @@ class ACARISTrainer(Trainer):
 	# 	print(f"metrics: {metrics}")
 	# 	return metrics
 
-	def compute_metrics(self, evalPred):
-		"""
-		This function computes various evaluation metrics such as accuracy, precision, recall, F1 score,
-		confusion matrix, and ROC AUC score for a given set of predicted and true labels.
-		
-		@param evalPred `evalPred` is an object of the `EvalPrediction` class which contains the predictions
-		and labels for a set of evaluation data. The `predictions` attribute contains the predicted logits
-		for each example in the evaluation set, and the `label_ids` attribute contains the true labels for
-		each example. The
-		
-		@return The function `compute_metrics` returns a dictionary containing various evaluation metrics
-		such as accuracy, confusion matrix, ROC AUC score, precision, recall, and F1 score for each label
-		(negative, neutral, and positive).
-		"""
-		logits, labels = evalPred.predictions, evalPred.label_ids
-		logits = torch.softmax(torch.Tensor(logits), dim=1)
-		preds = torch.argmax(logits, dim=1)
-		if len(labels) > 0:
-			acc = (preds == labels).sum().item() / len(labels)
-		else:
-			acc = 0
-		precision, recall, f1, _ = precision_recall_fscore_support(labels, preds, average=None)
-		accuracy = accuracy_score(labels, preds)
-		confMatrix = confusion_matrix(labels, preds)
-		rocAUC = roc_auc_score(labels, logits, multi_class="ovr")
-		metrics = {
-			"eval_accuracy": accuracy,
-			"confusion_matrix": confMatrix,
-			"roc_auc": rocAUC
-		}
-		metricNames = ["precision", "recall", "f1"]
-		labelNames = ["neg", "neu", "pos"]
-		for metricName, metricValue in zip(metricNames, [precision, recall, f1]):
-			for labelName, value in zip(labelNames, metricValue):
-				metrics[f"{metricName}_{labelName}"] = float(value)
-		print(f"metrics: {metrics}")
-		return metrics
-
 	def prediction_step(self, mdl, inputs: dict[str, torch.Tensor], prediction_loss_only, ignore_keys=None):
 		"""
 		This function performs a prediction step using a given model and inputs, and returns the loss,

### 2023-05-30 train.py

@@ -39,6 +39,44 @@ class MdlTrainer:
 		self.device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
 		wandb.watch(self.model, log="all")
 
+	def compute_metrics(self, evalPred):
+		"""
+		This function computes various evaluation metrics such as accuracy, precision, recall, F1 score,
+		confusion matrix, and ROC AUC score for a given set of predicted and true labels.
+		
+		@param evalPred `evalPred` is an object of the `EvalPrediction` class which contains the predictions
+		and labels for a set of evaluation data. The `predictions` attribute contains the predicted logits
+		for each example in the evaluation set, and the `label_ids` attribute contains the true labels for
+		each example. The
+		
+		@return The function `compute_metrics` returns a dictionary containing various evaluation metrics
+		such as accuracy, confusion matrix, ROC AUC score, precision, recall, and F1 score for each label
+		(negative, neutral, and positive).
+		"""
+		logits, labels = evalPred.predictions, evalPred.label_ids
+		logits = torch.softmax(torch.Tensor(logits), dim=1)
+		preds = torch.argmax(logits, dim=1)
+		if len(labels) > 0:
+			acc = (preds == labels).sum().item() / len(labels)
+		else:
+			acc = 0
+		precision, recall, f1, _ = precision_recall_fscore_support(labels, preds, average=None)
+		accuracy = accuracy_score(labels, preds)
+		confMatrix = confusion_matrix(labels, preds)
+		rocAUC = roc_auc_score(labels, logits, multi_class="ovr")
+		metrics = {
+			"eval_accuracy": accuracy,
+			"confusion_matrix": confMatrix,
+			"roc_auc": rocAUC
+		}
+		metricNames = ["precision", "recall", "f1"]
+		labelNames = ["neg", "neu", "pos"]
+		for metricName, metricValue in zip(metricNames, [precision, recall, f1]):
+			for labelName, value in zip(labelNames, metricValue):
+				metrics[f"{metricName}_{labelName}"] = float(value)
+		print(f"metrics: {metrics}")
+		return metrics
+
 	def fine_tune(self, trainLoader, valLoader, epochs, batchSize, outputDir):
 		"""
 		This function fine-tunes a given model using the provided training and validation data loaders, for
@@ -82,6 +120,7 @@ class MdlTrainer:
 			args=trainingArgs,
 			trainLoader=trainLoader,
[…]

### 2023-05-30 user_embedder.py

@@ -19,17 +19,13 @@ class UserEmbedder:
 
 	def get_user_embedding(self, uid) -> torch.Tensor:
 		"""
-		This function retrieves or creates a user embedding tensor based on the user's messages.
+		This function retrieves or creates a user embedding for a given user ID.
 		
 		@param uid uid stands for "user ID", which is a unique identifier assigned to each user in a system
-		or application. In this code, it is used to retrieve or create an embedding (a numerical
-		representation) for a specific user based on their messages.
+		or application. In this code, it is used to retrieve or create an embedding vector for a specific
+		user.
 		
-		@return a torch.Tensor object, which is the user embedding for the given user ID. If the user
-		embedding has already been computed and stored in memory, it is returned directly. Otherwise, the
-		function extracts features from the user's messages, creates a user embedding from these features,
-		and stores the embedding in memory and on disk before returning it. If there are no messages for the
-		given user ID
+		@return a torch.Tensor object, which represents the embedding of a user with the given uid.
 		"""
 		path = os.path.join("./userEmbeddings", f"{uid}.pt")
 

### 2023-05-30 train.py
add

@@ -4,7 +4,7 @@ This module trains.
 
 import torch
 from torch.utils.data import DataLoader
-from transformers import AutoModelForSequenceClassification, Trainer, TrainingArguments
+from transformers import AutoModelForSequenceClassification, Trainer, TrainingArguments, AutoTokenizer, EvalPrediction
 from acaris_mdl import ACARISMdl
 from acaris_ds import ACARISDs
 from acaris_trainer import ACARISTrainer
@@ -18,6 +18,7 @@ import wandb
 from acaris_trainer import ProgressCb
 from alert import send_alert
 import socket
+from sklearn.metrics import accuracy_score, f1_score, precision_recall_fscore_support, confusion_matrix, roc_auc_score, classification_report
 
 os.environ["TOKENIZERS_PARALLELISM"] = "false"
 #os.environ["CUDA_LAUNCH_BLOCKING"] = "1"

### 2023-05-31 inferACARIS.py
established and trained the very first ACARIS model\!

@@ -1,0 +1,39 @@
+import torch
+from transformers import DistilBertTokenizerFast
+from user_embedder import UserEmbedder
+from trainACARIS import DistilBertForMulticlassSequenceClassification
+
+
+class InferACARIS:
+	def __init__(self, mdlPath):
+		self.model = DistilBertForMulticlassSequenceClassification.from_pretrained(mdlPath)
+		self.tokenizer = DistilBertTokenizerFast.from_pretrained("distilbert-base-uncased")
+		self.userEmbedder = UserEmbedder(userEmbeddingSize=11)
+		self.device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
+		self.model.to(self.device)
+
+	def predict(self, uids, contents):
+		userEmbs = [self.userEmbedder.get_user_embedding(uid) for uid in uids]
+		inputs = self.tokenizer(contents, truncation=True, padding="max_length", max_length=128, return_tensors="pt")
+		inputs = {name: tensor.to(self.device) for name, tensor in inputs.items()}
+		userEmbs = torch.stack(userEmbs).to(self.device)
+
+		self.model.eval()
+		with torch.no_grad():
+			outputs = self.model(input_ids=inputs["input_ids"], attention_mask=inputs["attention_mask"], userEmbs=userEmbs)
+
+		probs = torch.nn.functional.softmax(outputs.logits, dim=1).cpu().numpy()
+		preds = outputs.logits.argmax(dim=1).cpu().numpy()
+
+		id2label = {0: "neg", 1: "neu", 2: "pos"}
+		labels = [id2label[pred] for pred in preds]
+
+		return labels, probs
+
+
+if __name__ == "__main__":
+	infer = InferACARIS("./output/checkpoint-3540/")
+	uids = ["Reknez#9257"]
+	contents = ["ok"]
+	labels, probs = infer.predict(uids, contents)
+	print(labels, probs)

### 2023-05-31 trainACARIS.py

@@ -1,0 +1,193 @@
+"""
+This mod fine-tunes a DistilBERT model on the ACARIS dataset with user embeddings, resulting in an ACARIS model.
+"""
+
+import torch
+from torch import nn
+from torch.utils.data import Dataset, DataLoader
+from transformers import DistilBertTokenizerFast, DistilBertForSequenceClassification, TrainingArguments, Trainer, AdamW, EarlyStoppingCallback, PreTrainedModel, DistilBertModel
+from transformers.modeling_outputs import SequenceClassifierOutput
+from datasets import load_dataset, Dataset
+import pandas as pd
+from sklearn.metrics import accuracy_score, precision_recall_fscore_support, confusion_matrix, roc_auc_score
+import wandb
+import huggingface_hub
+import os
+import random
+import numpy as np
+from user_embedder import UserEmbedder
+
+config = {
+	"mdl": "distilbert-base-uncased",
+	"epochs": 5,
+	"batchSize": 14,
+	"maxLen": 512,
+	"warmupSteps": 0.1, # proportion of total steps, NOT absolute
+	"weightDecay": 0.02,
+	"outputDir": "./output",
+	"earlyStopping": True,
+	"earlyStoppingPatience": 2,
+	"dropout": 0.1,
+	"initlr": 5e-5,
+	"epsilon": 1e-8
+}
+
+wandb.init(project="MarkIII_ACARIS", entity="simtoonia", config=config)
+
+
+def lockSeed(seed):
+	random.seed(seed)
+	np.random.seed(seed)
+	torch.manual_seed(seed)
+	if torch.cuda.is_available():
+		torch.cuda.manual_seed_all(seed)
+		torch.backends.cudnn.deterministic = True
+
+#0 disabled, as determinism is not guaranteed and lowers performance
+#lockSeed(69) # setting a fixed seed for *some* reproducibility
+
+class DistilBertForMulticlassSequenceClassification(DistilBertForSequenceClassification):
+	def __init__(self, config):
+		super().__init__(config)
+		self.userEmbSize = 11
+		self.userEmb = nn.Linear(self.userEmbSize, config.dim)
+		self.small = nn.Linear(config.dim * 2, config.dim)
+
+	def forward(self, input_ids=None, attention_mask=None, userEmbs=None, head_mask=None, inputs_embeds=None, labels=None, output_attentions=None, output_hidden_states=None, return_dict=None):
[…]

### 2023-05-31 trainDistilBERT.py

@@ -81,8 +81,6 @@ class ACARISBERT:
         self.tokenizer = DistilBertTokenizerFast.from_pretrained(config["mdl"])
         self.model = DistilBertForMulticlassSequenceClassification.from_pretrained(config["mdl"], num_labels=3, id2label={0: "neg", 1: "neu", 2: "pos"}, label2id={"neg": 0, "neu": 1, "pos": 2}, dropout=config["dropout"], attention_dropout=config["dropout"])
 
-
-
     def read_data(self, path):
         df = pd.read_csv(path, sep="|", usecols=["content", "sentiment"])
         return Dataset.from_pandas(df)
@@ -110,11 +108,11 @@ class ACARISBERT:
         preds = torch.argmax(torch.Tensor(logits), dim=1)
         precision, recall, f1, _ = precision_recall_fscore_support(labels, preds, average=None)
         accuracy = accuracy_score(labels, preds)
-        confMatrix = confusion_matrix(labels, preds)
+        #confMatrix = confusion_matrix(labels, preds)
         rocAUC = roc_auc_score(labels, preds, multi_class="ovr")
         metrics = {
             "accuracy": accuracy,
-            "confusion_matrix": confMatrix,
+            #"confusion_matrix": confMatrix,
             "roc_auc": rocAUC
         }
         metricNames = ["precision", "recall", "f1"]

### 2023-05-31 upload.py

@@ -1,0 +1,18 @@
+from transformers import DistilBertTokenizerFast
+import sys
+from trainACARIS import DistilBertForMulticlassSequenceClassification
+import os
+
+class InferACARISBERT:
+	def __init__(self, mdlPath):
+		self.mdlPath = mdlPath
+		self.tokenizer = DistilBertTokenizerFast.from_pretrained("distilbert-base-uncased")
+		self.model = DistilBertForMulticlassSequenceClassification.from_pretrained(self.mdlPath)
+
+	def push(self, modelName, org="ongknsro"):
+		self.model.push_to_hub(repo_id=f"{org}/{modelName}", private=True)
+		self.tokenizer.push_to_hub(repo_id=f"{org}/{modelName}")
+
+if __name__ == "__main__":
+	acaris_bert_infer = InferACARISBERT("./output/checkpoint-3540")
+	acaris_bert_infer.push("ACARIS-DistilBERT-iter1-fp16-batchSize14")

### 2023-06-10 paper.tex
Made some progress, almost made ACARIS work. good job, me ... LOL
concluded the prelim work for the UCL thesis; a lot more work done, including a comparer class for measuring perf diff betweewn ACARIS and baseline

--- 2023-05-18 paper.tex
@@
 \documentclass{article}
-\usepackage[utf8]{inputenc}
+\usepackage{csquotes}
+\usepackage[english]{babel}
 \usepackage{amsmath}
@@
 \usepackage{multirow}
+\usepackage{microtype}
 \usepackage[backend=biber, sorting=none]{biblatex}
+\usepackage{listings}
+\lstset{breaklines=true,basicstyle=\footnotesize,language=Python}
+\usepackage[normalem]{ulem}
 \addbibresource{refs.bib}
+\AtBeginBibliography{\raggedright}
 %\usepackage{multicol}
+\usepackage{emoji}
 
@@
 \small\textbf{OngakkenAI}}
-\date{June 1, 2023}
+\date{June 21, 2023}
 
@@
 ACARIS is being built with the goal of improving social skills of humans, while also improving the performance of human-facing AI systems.
-We go over our approach, including the initialization of user embeddings from message features, concatenation of user embeddings with word embeddings, modifications of the BERT architecture, and the training and evaluation processes.
-We also go over the results of our experiments, which demonstrate the effectiveness of our method.
+We go over our initial approach, including the initialization of user embeddings from message features, concatenation of user embeddings with word embeddings, modifications of the DistilBERT architecture, and the training and evaluation processes.
+We also go over the results of our experiments.
+Presently, we are not able to achieve any statistically nor practically significant improvement over the current state-of-the-art.
+However, we actively continue to work on improving our approach by iterating over different architectures, hyperparameters, and user embedding forms.
+In addition, the work currently only handles sentiment analysis, as other tasks are still in heavy development.
+As such, the target variable of the model is a sentiment label, and as such, the model is a classifier.
 \end{abstract}
@@
 	\item \textbf{ACARIS} - the Advanced Communication Augmentor and Relational Insights System
-	\item \textbf{NLP} - Natural Language Processing - a subfield of linguistics, computer science, and artificial intelligence concerned with the interactions between computers and human language, in particular how to program computers to process and analyze large amounts of natural language data
-	\item \textbf{Deep Learning} - a class of machine learning algorithms that uses multiple layers to progressively extract higher-level features from the raw input
+	\item \textbf{NLP} - Natural Language Processing - a subfield of linguistics, computer science, and artificial intelligence concerned with the interactions between machines and human language, in particular how to program computers to process and analyze large amounts of natural language data
+	\item \textbf{Deep learning} - a class of machine learning algorithms that uses multiple layers to progressively extract higher-level features from the raw input
+	\item \textbf{Paired t-test} - a statistical procedure used to determine whether the mean difference between two sets of observations is zero
+	\item \textbf{Shapiro-Wilk test} - a test of normality in frequentist statistics
+	\item \textbf{p-value} - the probability of obtaining results as extreme as the observed results of a statistical hypothesis test, assuming that the null hypothesis is correct
+	\item \textbf{Wilcoxon signed-rank test} - a non-parametric statistical hypothesis test used when comparing two related samples, matched samples, or repeated measurements on a single sample to assess whether their population mean ranks differ
+	\item \textbf{Decision boundary} - a hypersurface that partitions the underlying vector space into two sets, one for each class
+	\item \textbf{model accuracy score} - the fraction of predictions a model got right
+	\item \textbf{model precision score} - the fraction of positive predictions a model got right
+	\item \textbf{model recall score} - the fraction of positive cases a model got right
+	\item \textbf{model support score} - the number of occurrences of each class in y\_true
+	\item \textbf{model F1 score} - the harmonic mean of precision and recall
+	\item \textbf{ROC curve} - the Receiver Operating Characteristic curve
+	\item \textbf{model AUC score} - the area under the ROC curve - a plot of the true positive rate against the false positive rate
 	\item \textbf{SVM} - Support Vector Machine - a supervised machine learning model that uses classification algorithms for two-group classification problems
-	\item \textbf{DT} - Decision Tree - 
+	\item \textbf{DT} - Decision Tree - a decision support tool that uses a tree-like model of decisions and their possible consequences
 	\item \textbf{LogReg} - Logistic Regression - a statistical model that in its basic form uses a logistic function to model a binary dependent variable, although many more complex extensions exist
 	\item \textbf{RF} - Random Forest - an ensemble learning method for classification, regression and other tasks that operate by constructing a multitude of decision trees at training time and outputting the class that is the mode of the classes (classification) or mean prediction (regression) of the individual trees
-	\item \textbf{TF-IDF} - Term Frequency - Inverse Document Frequency - a numerical statistic that is intended to reflect how important a word is to a document in a collection or corpus
+	\item \textbf{TF-IDF} - Term Frequency - Inverse Document Frequency - a numerical statistic that is intended to reflect how important a word is to a document in a collection or corpus, calculated as the product of its term frequency and its inverse document frequency.
+Has no sense of word order
 	\item \textbf{the Transformer} - a deep learning architecture introduced in 2017, used primarily in the field of NLP\cite{vaswani2017attention}
 	\item \textbf{BERT} - Bidirectional Encoder Representations from Transformers - a transformer-based machine learning model for natural language processing pre-training developed by Google\cite{devlin2019bert}
-	\item \textbf{DistilBERT} - DistilBERT is a smaller, faster, cheaper version of BERT developed by HuggingFace\cite{sanh2020distilbert}
+	\item \emoji{hugging-face} - Hugging Face - a company that develops and maintains open-source libraries for natural language processing
+	\item \textbf{DistilBERT} - DistilBERT is a smaller, faster, cheaper version of BERT developed by \emoji{hugging-face}\cite{sanh2020distilbert}
 	\item \textbf{Vector} - a quantity that has both magnitude and direction
-	\item \textbf{Vector Space} - a collection of vectors, which may be added together and multiplied ("scaled") by numbers, called scalars
-	\item \textbf{Embedding Space} - a vector space with a coordinate for each word in the vocabulary, such that words that share common contexts in the corpus are located close to one another in the space
-	\item \textbf{Word Embedding} - A vector representation of a word's meaning
-	\item \textbf{User Embedding} - A vector representation of a user's personality, emotional state, intent, and interest
+	\item \textbf{Vector space} - a collection of vectors, which may be added together and multiplied ("scaled") by numbers, called scalars
+	\item \textbf{Embedding space} - a vector space with a coordinate for each word in the vocabulary, such that words that share common contexts in the corpus are located close to one another in the space
+	\item \textbf{Word embedding} - A vector representation of a word's meaning
+	\item \textbf{User embedding} - A vector representation of a user's personality, emotional state, intent, and interest
+	\item \textbf{FFNN} - Feed-Forward Neural Network - a neural network where connections between units do not form a cycle
 	\item \textbf{ReLU} - Rectified Linear Unit - an activation function that returns the input value if it is positive, otherwise it returns zero
 	\item \textbf{Loss} - a number indicating how bad the model's prediction was on a single example
-	\item \textbf{Cross-Entropy Loss} - a loss function used for classification problems
+	\item \textbf{Cross-entropy loss} - negative logarithmic likelihood loss - a loss function used for classification problems
 	\item \textbf{Adam} - an optimization algorithm that can be used instead of the classical stochastic gradient descent procedure to update network weights
-	\item \textbf{Ablation Study} - a study in which specific components of a system are removed to analyze their impact on the overall performance
 \end{itemize}
@@
 
-\subsection{Hypothesis}
-Given enough conversational data per person, human behavior (emotional state, intent) in text communication can be predicted with a high level of confidence ($>80\%$) due to the fact that humans are, on a fundamental level, very similar to one another.
+\subsection{Hypotheses}
+\subsubsection{$H_1$}
+Given enough conversational data per person, human behavior (personality, emotional state, intent, and interest rate) in text communication can be predicted with a high level of confidence ($>80\%$) due to the fact that humans are, on a fundamental level, very similar to one another.
 
-Additionally, we posit that person-specific performance improvements can be achieved by individualizing predictions by using a unique vector representation of a person's personality, emotional state, intent, and interest, which we call a user embedding.
+Additionally, we posit that person-specific performance improvements can be achieved by individualizing predictions by using a unique vector representation of a person's personality, emotional state, intent, and interest rate, which we call a user embedding.
 The postulate stems in the core concept of neural networks being universal function approximators.
 Therefore, in theory, a neural network should be able to learn to associate a user embedding with a person's behavior in text communication and use that information to improve its predictions.
+
+\subsubsection{$H_0$}
+The performance of a human behavior analysis model trained using a user embedding is not significantly different from the performance of a human behavior analysis model trained purely with input sequences as the model's input.
+
+\subsubsection{Statistical significance}
+To test the statistical significance between the ACARIS and the baseline models, we use paired t-tests or, if the metrics are not normally distributed, Wilcoxon signed-rank tests.
+A p-value of $<0.05$ is considered statistically significant.
+
+\subsubsection{Practical significance}
+To test the practical significance between the ACARIS and the baseline models, we define a decision boundary of practical significance as a model performance improvement of the ACARIS model over the baseline model of $>=5\%$ across all calculated model performance metrics, simultaneously.
+Namely, these are accuracy, precision, recall, F1, and AUC.
 
@@
 	\item \textbf{Transformers for Natural Language Processing}\cite{rothman2022transformers} by Denis Rothman, Antonio Gulli
+	\item \textbf{Transformers for Machine Learning: A Deep Dive}\cite{kamath2022transformers} by Uday Kamath, Kenneth L. Graham, Wael Emara
 \end{itemize}
@@
 
-\subsection{Initial Attempts}
+\subsection{Initial attempts}
 Our initial attempts of implementing ACARIS included the use of SVMs, DTs, LogReg, and RFs, each paired with TF-IDF in the preprocessing stage.
@@
 For sequential data, RNNs and CNNs were classically used.
-However, due to the long-term dependency problem of RNNs, we made the decision to not use them, as we believed that they would not be able to capture the long-term dependencies in our dataset.
-Additionally, we weren't able to guarantee that during inference, there would be no long-term dependencies.
-Another issue was TF-IDF's lack of word order understanding.
-Knowing that the Transformer\cite{vaswani2017attention} architecture is capable of capturing these aspects due to its positional encodinds and self-attention mechanism, we decided to use it as the basis for ACARIS.
+However, due to the long-range dependency problem of RNNs, we made the decision to not use them, as we believed that they would not be able to capture the long-range dependencies in our dataset.
+Additionally, we weren't able to guarantee that during inference, there would be no long-range dependencies.
+Another issue was TF-IDF's lack of word order and semantic meaning understanding.
+Knowing that the Transformer\cite{vaswani2017attention} architecture is capable of capturing these aspects due to its positional encodings and self-attention mechanism, we decided to use it as the basis for ACARIS.
 
-\subsection{Short Intro on Transformers}
-The Transformer is a deep learning model proposed in 2017 by a team of Google Brain/Google Research researchers.
+\subsection{Short intro on Transformers}
+The Transformer is a deep learning model architecture proposed in 2017 by a team of Google Brain/Google Research researchers.
 It is mainly used in NLP, but it has also found its way into numerous vision projects (Latent Diffusion\cite{rombach2021highresolution}/Stable Diffusion/LLaVA\cite{liu2023visual}, to name a few).
+The architecture aims to replace RNNs by using attention mechanisms (self-attention, in particular) and positional encodings to model long-range dependencies in sequential data.
 
@@
 
-% features:
-% - Mean wordcount (per msg)
-% - Vocab richness (type-token ratio?) - Unique words / total words
-% - Mean emoji count (per msg)
-% - Mean emoticon count (per msg)
-% - Mean punctuation count (per msg)
-% - Mean sentiment score (per msg)
-% - Dominant/prevalent topics
-% - Mean response time (!exclude closing messages, such as "Goodnight")
-% - Mean message count (per day)
-% - Mean links (per msg)
-% - Mean markdown code snippet sections (per msg)
-% - Mean abbreviations and acronyms (per msg) (such as "lol", "omg", "FBI", ...)
-% - Mean hashtag count (per msg)
-
 \subsection{Dataset}
-To build our dataset, we collected 100 thousand messages from our Discord server, classified them into 3 classes (pos, neg, neu), and augmented them with the GoEmotions\cite{demszky2020goemotions} dataset, which contains 58 thousand messages classified into 27 classes.
-We squashed the 27 classes into 3 classes (pos, neg, neu) and concatenated the two datasets.
+To build our dataset, we collected ~65 thousand messages from our Discord server, classified them into 3 classes (pos, neg, neu), and augmented the dataset with the following additional datasets: GoEmotions\cite{demszky2020goemotions} dataset, which contains 58 thousand messages classified into 27 classes.
+We squashed the 27 classes into 3 classes (pos, neg, neu); Twitter Sentiment and Emotion Analysis\cite{Cop_2021} containing 6032 rows of tweets labeled positive, negative, and neutral; Twitter-Sentiment Data\cite{Kumar_2022} containing 1975 rows of tweets labeled into the same three classes.
 To minimize error caused by input data, we removed all users with less than 25 messages, URLs, markdown code blocks, Discord mentions and custom emoji, and attachments.
-The resulting dataset was split into 75\% training, 10\% validation, and 15\% test sets.
+We also removed all messages shorter than 25 characters.
+The resulting dataset was split into 75\% training, 17\% validation, and 8\% test sets, and contains 24769, 5504, and 2753 rows, respectively (filtered).
+The discrepancy most likely stems in our splitting algorithm's static seed.
+The dataset is not publicly available at the moment due to the sensitive nature of the data.
 
@@
 	\item \textbf{Mean sentiment score (per all $m$)} - \(\overline{s} = \frac{1}{N} \sum_{i=1}^{N} s_i \), where $s_i$ is the sentiment score of $i$-th message and $N$ is the total number of messages
-	\item \textbf{Dominant/prevalent topics (per all $m$)} - the most common topics in all messages
-	\item \textbf{Mean response time (per all $m$)} - \(\overline{r} = \frac{1}{N} \sum_{i=1}^{N} r_i \), where $r_i$ is the response time of $i$-th message and $N$ is the total number of messages
+	\item \sout{Dominant/prevalent topics (per all $m$) - the most common topics in all messages}
+	\item \sout{Mean response time (per all $m$} - \(\overline{r} = \frac{1}{N} \sum_{i=1}^{N} r_i \), where $r_i$ is the response time of $i$-th message and $N$ is the total number of messages
 	\item \textbf{Mean message count (per day)} - \(\overline{m} = \frac{1}{D} \sum_{i=1}^{D} m_i \), where $m_i$ is the message count of $i$-th day and $D$ is the total number of days
 	\item \textbf{Mean links (per all $m$)} - \(\overline{l} = \frac{1}{N} \sum_{i=1}^{N} l_i \), where $l_i$ is the link count of $i$-th message and $N$ is the total number of messages
-	\item \textbf{Mean markdown code snippet sections (per all $m$)} - \(\overline{c} = \frac{1}{N} \sum_{i=1}^{N} c_i \), where $c_i$ is the markdown code snippet section count of $i$-th message and $N$ is the total number of messages
+	\item \sout{Mean markdown code snippet sections (per all $m$) - \(\overline{c} = \frac{1}{N} \sum_{i=1}^{N} c_i \), where $c_i$ is the markdown code snippet section count of $i$-th message and $N$ is the total number of messages}
 	\item \textbf{Mean abbreviations and acronyms (per all $m$)} - \(\overline{a} = \frac{1}{N} \sum_{i=1}^{N} a_i \), where $a_i$ is the abbreviation and acronym count of $i$-th message and $N$ is the total number of messages
-	\item \textbf{Mean hashtag count (per all $m$)} - \(\overline{h} = \frac{1}{N} \sum_{i=1}^{N} h_i \), where $h_i$ is the hashtag count of $i$-th message and $N$ is the total number of messages
+	\item \sout{Mean hashtag count (per all $m$) - \(\overline{h} = \frac{1}{N} \sum_{i=1}^{N} h_i \), where $h_i$ is the hashtag count of $i$-th message and $N$ is the total number of messages}
+	\item \textbf{Mean noun count (per all $w$ in all $m$)} - \(\overline{n} = \frac{1}{W} \sum_{i=1}^{W} n_i \), where $n_i$ is the noun count of $i$-th word and $W$ is the total number of words
+	\item \textbf{Mean verb count (per all $w$ in all $m$)} - \(\overline{v} = \frac{1}{W} \sum_{i=1}^{W} v_i \), where $v_i$ is the verb count of $i$-th word and $W$ is the total number of words
+	\item \textbf{Mean adjective count (per all $w$ in all $m$)} - \(\overline{adj} = \frac{1}{W} \sum_{i=1}^{W} adj_i \), where $adj_i$ is the adjective count of $i$-th word and $W$ is the total number of words
 \end{itemize}
 These features were selected based on what we thought would most accurately represent a user's text communication behavior.
-We projected that no two users would have the same or closely similar values for all of these features, which would allow us to differentiate between them.
+We projected that no two users would have the same or closely similar values for all of these features, which would allow us to differentiate between them.\\
 Then, we concatenate all the features into a single vector $e_u$ (of size $d_e$):
@@
 	&\text{\texttt{from torch import cat}} \\
-&e_u = \textnormal{\texttt{cat}}([\overline{w}, r, \overline{e}, \overline{em}, \overline{p}, \overline{s}, \overline{r}, \overline{m}, \overline{l}, \overline{c}, \overline{a}, \overline{h}], \textnormal{dim}=-1)
+	&e_u = \textnormal{\texttt{cat}}([\overline{w}, r, \overline{e}, \overline{em}, \overline{p}, \overline{s}, \overline{m}, \overline{l}, \overline{a}, \overline{n}, \overline{v}, \overline{adj}], \textnormal{dim}=-1)
 	\end{aligned}
 \end{equation}
-\subsection{Concatenation of User and Word Embeddings}
+\subsection{Concatenation of user and word embeddings}
 Given a message $m$ with its word embedding $e_w$ (of size $d_m$) from a BERT-like pre-trained model, which, in our case, was DistilBERT\cite{sanh2020distilbert}, we concatenate the user embedding $e_u$ to the word embedding $e_w$ to create a joint representation $e_\textnormal{joint}$ (of size $d_e + d_m$):
@@
 \end{equation}
-
-\subsection{Model Architecture Modification}
-To accommodate the concatenated embeddings, we create a custom input layer with the new input size $d_e + d_m$ within a BERT-flavored model.
-An alternative that we thought of using was to use a separate fully-connected layer (with ReLU activation) to map the concatenated embeddings to a compatible size:
+\subsection{Model architecture modification}
+To accommodate the concatenated embeddings, we create a custom FFNN, as such:
 \begin{equation}
 	\begin{aligned}
-&\text{\texttt{from torch import randn}} \\
-&\text{\texttt{from torch import relu}} \\
-&\text{\texttt{from torch import matmul}} \\
-&W1 = \text{\texttt{randn}}((d_e + d_m, d_m)) \\
-&b1 = \text{\texttt{randn}}(d_m) \\
-&e_\textnormal{map} = \text{\texttt{relu}}(\text{\texttt{matmul}}(e_\textnormal{joint}, W1) + b1)
+	&\text{\texttt{from torch.nn import Linear, ReLU, LayerNorm, Dropout}} \\
+	&h_{1} = \text{\texttt{Linear}}_{\text{\texttt{$d_e$, 512}}}(e_u) \\
+	&h_{1} = \text{\texttt{ReLU}}(h_{1}) \\
+	&h_{2} = \text{\texttt{Linear}}_{\text{\texttt{512, $d_m$}}}(h_{1}) \\
+	&h_{2} = \text{\texttt{LayerNorm}}_{\text{\texttt{$d_m$}}}(h_{2}) \\
+	&h_{2} = \text{\texttt{Dropout}}_{\text{\texttt{0.1}}}(h_{2}) \\
+	&h_{3} = \text{\texttt{Linear}}_{\text{\texttt{$d_m$, 512}}}(h_{2}) \\
+	&h_{3} = \text{\texttt{ReLU}}(h_{3}) \\
+	&h_{3} = \text{\texttt{LayerNorm}}_{\text{\texttt{512}}}(h_{3}) \\
+	&h_{3} = \text{\texttt{Dropout}}_{\text{\texttt{0.1}}}(h_{3}) \\
+	&e'_u = \text{\texttt{Linear}}_{\text{\texttt{512, $d_m$}}}(h_{3}) \\
 	\end{aligned}
 \end{equation}
-Then, pass $e_\textnormal{map}$ through the existing model architecture.
+The FFNN contains 3 layers, each with a ReLU activation function, a layer normalization, and dropout for regularization.
+The first linear (dense) layer is a function $y = xw + b$, where $x$ is a user embedding vector, that takes in the $d_e$-dimensional user embedding and learns to transform it to a dimensionality of 512.
+After the first linear transformation, ReLU will return 0 if its input is negative, and the value of the input if it's 0 or positive.
+This operation is applied element-wise and introduces non-linearity to the model.
+The second linear layer transforms its input from 512 to $d_m$, which is the dimensionality of our word embedding, and is of value 768.
+Layer normalization normalizes the features of the output of the linear layer to have a mean of 0 and a standard deviation of 1 to stabilize the learning process.
+Dropout will randomly set some of the activations to 0 (with a probability of 0.1), which helps with preventing overfitting by forcing the model to learn a more robust representation of the data.
+The third linear layer transforms its input from $d_m$ back to 512. We, once again, apply a ReLU, layer normalization, and dropout.
+The final linear layer reduces its input dimensionality to $d_m$, which is 768. The output of the FFNN is the user embedding $e'_u$ (of size $d_m$).\\
+\\
+\\
+The following is the model definition:\\
 
-\subsection{Training with User Embeddings}
-For each training step, we pass the concatenated embeddings $e_\textnormal{joint}$ through the model and compute the cross-entropy loss $L$.
-Then, we backpropagate the gradients from the loss to the model parameters and update the parameters using Adam.
+\begin{lstlisting}
+class DistilBertForMulticlassSequenceClassification(DistilBertForSequenceClassification):
+def __init__(self, config):
+	super().__init__(config)
+	self.userEmbSize = 12
+	self.pre_classifier = nn.Linear(config.dim * 2, config.dim) # '2' because of the concat, which doubles the input size to that of the pre_classifier
+	self.classifier = nn.Linear(config.dim, 3) # '3' for our 3 classes
+	self.userEmb = nn.Sequential(
+		nn.Linear(self.userEmbSize, 512),
+		nn.ReLU(),
+		nn.Linear(512, config.dim), # config.dim.shape = (768,)
+		nn.LayerNorm(config.dim),
+		nn.Dropout(0.1),
+		nn.Linear(config.dim, 512),
+		nn.ReLU(),
+		nn.LayerNorm(512),
+		nn.Dropout(0.1),
+		nn.Linear(512, config.dim)
+	)
+
+def forward(self, input_ids=None, attention_mask=None, userEmbs=None, head_mask=None, inputs_embeds=None, labels=None, output_attentions=None, output_hidden_states=None, return_dict=None):
+	return_dict = return_dict if return_dict is not None else self.config.use_return_dict
+
+	outputs = self.distilbert(input_ids, attention_mask=attention_mask, head_mask=head_mask, inputs_embeds=inputs_embeds, output_attentions=output_attentions, output_hidden_states=output_hidden_states, return_dict=return_dict)
+
+	hidden_state = outputs[0]
+
+	userEmbs = self.userEmb(userEmbs)
+	userEmbsRep = userEmbs.unsqueeze(1).repeat(1, hidden_state.size(1), 1)
+	hidden_state = torch.cat((hidden_state, userEmbsRep), dim=-1)
+	pooled_output = hidden_state[:, 0]
+	pooled_output = self.pre_classifier(pooled_output)
+	pooled_output = nn.ReLU()(pooled_output)
+	pooled_output = self.dropout(pooled_output)
+	logits = self.classifier(pooled_output)
+
+	loss = None
+	if labels is not None:
+		lossFct = nn.CrossEntropyLoss()
+		loss = lossFct(logits.view(-1, self.num_labels), labels.view(-1))
+
+	if not return_dict:
+		output = (logits,) + outputs[2:]
+		return ((loss,) + output) if loss is not None else output
+
+	return SequenceClassifierOutput(loss=loss, logits=logits, hidden_states=outputs.hidden_states, attentions=outputs.attentions)
+\end{lstlisting}
+
+The $userEmbsRep$ variable is created to associate a user embedding with each token in an input sequence.
+Initially, the user embedding is a matrix of shape $(batchSize, userEmbSize)$.
+To associate the user embedding with each token, we need to repeat it along a third dimension, which we need to add, making the user embedding a 3D tensor.
+We first add a singleton dimension to the position 1 using the unsqueeze() method, changing the shape to $(batchSize, 1, userEmbSize)$, and subsequently repeat the user embedding along this dimension using the repeat() method, changing the second dimension from $1$ to $seqLen$ (input sequence length), as such $(batchSize, seqLen, userEmbSize)$.
+The unsqueeze() method doesn't affect the data inside the tensor, only its shape.
+This resulting user embedding is then concatenated with the model's hidden state, which represents word embeddings for all tokens in an input sequence, along the last dimension.
+
+\subsection{Training with user embeddings}
+For each training step, we pass the concatenated embeddings $e_\textnormal{joint}$ through the model and compute the cross-entropy loss $L$ (negative logarithmic likelihood).
+Then, we backpropagate gradients from the loss to the model parameters and update the parameters using Adam.
 The model thus learns to associate every message $m$ with a user embedding $e_u$ and a sentiment label $y$.
 
-\subsection{Updating User Embeddings}
+\subsection{Updating user embeddings}
 The user embeddings $e_u$ are not updated during training.
-Instead, they are pre-computed during data preprocessing and stored in an embedding matrix.
+Instead, they are pre-computed during data preprocessing and stored in a .pt file, one file per user.
 We repeat training every week, using new data from the previous week to update the user embeddings $e_u$.
@@
 \section{Evaluation}
-NaN
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth,height=6.5cm]{images/baseline.png}
+	\caption{Baseline model performance\cite{wandb}}
+	\label{fig:baseline}
+\end{figure}
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth,height=6cm]{images/ACARIS.png}
+	\caption{ACARIS model performance\cite{wandb}}
+	\label{fig:ACARIS}
+\end{figure}
 
 \section{Validation}
-To validate our approach, we compared the performance of our model with the performance of a baseline model.
-We used the same model, DistilBERT, but without the user embeddings $e_u$.
-We fine-tuned both models on the same dataset and compared their performance on the same test set.
+To validate our approach, we compare the performance of our model to the performance of a baseline model.
+We use the same model, DistilBERT, but without user embeddings $e_u$.
+We fine-tune both models on the same dataset and compared their performance on the same test set.\\\\
+The base model performed as follows:
+\begin{lstlisting}
+	Baseline metrics:
+              precision    recall  f1-score   support
+
+         neg       0.88      0.90      0.89      1514
+         neu       0.63      0.47      0.54       461
+         pos       0.81      0.89      0.85       778
+
+    accuracy                           0.83      2753
+   macro avg       0.77      0.75      0.76      2753
+weighted avg       0.82      0.83      0.82      2753
+
+[[1369   85   60]
+ [ 146  217   98]
+ [  45   44  689]]
+ROC AUC: 0.9355478295192009
+Log loss: 0.43026491940343037
+\end{lstlisting}
+The ACARIS model performed as follows:
+\begin{lstlisting}
+	ACARIS metrics:
+              precision    recall  f1-score   support
+
+         neg       0.89      0.90      0.89      1514
+         neu       0.62      0.50      0.55       461
+         pos       0.81      0.88      0.85       778
+
+    accuracy                           0.83      2753
+   macro avg       0.77      0.76      0.77      2753
+weighted avg       0.82      0.83      0.82      2753
+
+[[1361   90   63]
+ [ 134  232   95]
+ [  36   54  688]]
+ROC AUC: 0.9343263777788224
+Log loss: 0.43922137166238784
+\end{lstlisting}
+\break
 \section{Results}
-NaN
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth,height=6cm]{images/confusion_matrix.png}
+	\caption{The confusion matrix of both models}
+	\label{fig:Conf}
+\end{figure}
+Both models performed similarly.
 
 \section{Conclusion}
-NaN
+Given all the information and performance metrics presently available as a result of the current implementation, we must conclude that we failed to reject the null hypothesis $H_0$, and as such, in this particular work, rejected the hypothesis $H_1$.
+The ACARIS model does not exhibit any statistically nor practically significant improvements over the baseline model.
+
+\section{Future work}
+Generally speaking, we still believe that the first part of the hypothesis $H_1$ applies, and that individualizing model outputs to each user is the way to go.
+It's just a matter of data sufficiency and correct approach.
+We plan to continue experimenting with various pre-trained models, especially those released in the recent weeks, such as the Falcon-40B\cite{falcon40b}, which performs incredibly well on eval tests, such as the ARC (25-shot)\cite{clark2018think}, HellaSwag (10-shot)\cite{zellers2019hellaswag}, and MMLU (5-shot)\cite{hendrycks2021measuring}, and is presently the number one open-source model\cite{open-llm-leaderboard} in terms of its performance.
+The recent weeks have also seen numerous optimization techniques that enable more efficient training of larger language models, so even with our limited hardware, we are able to fine-tune models of 13B and more parameters.
+In addition, we also want to rethink our approach to user embeddings, and perhaps learn them during training, if we find a way to do so efficiently.
+Until then, we'll continue working with pre-computed user embeddings, but will expand them to add more complexity.
+Another area of improvement, in our opinion, is the concatenation operation.
+We believe that summation may offer different results, and will try to implement it in the future.
+Finally, and this is the most important factor, is the lack of user-specific data.
+We don't presently have sufficient messages for many users to train a model that generalizes well.
+We suspect that this is the main reason why our model failed to outperform the baseline model.
+\newpage
 
 \printbibliography
-
 %\end{multicols}
-
 \end{document}

### 2023-06-10 acaris_comparer.py

@@ -1,17 +1,31 @@
-from sklearn.metrics import classification_report, confusion_matrix, roc_auc_score, log_loss
+from sklearn.metrics import classification_report, confusion_matrix, roc_auc_score, log_loss, precision_recall_fscore_support, accuracy_score
 from sklearn.preprocessing import label_binarize
 from inferDistilBERT import InferACARISBERT
 from inferACARIS import InferACARIS
 import pandas as pd
 import numpy as np
 from tqdm import tqdm
+import scipy.stats as stats
+from scipy.stats import probplot
+import seaborn as sns
+import matplotlib
+import matplotlib.pyplot as plt
+matplotlib.use("TkAgg")
+from termcolor import colored
+import os
+
+classLabels = ["neg", "neu", "pos"]
 
 
 
 class ACARISComparer:
-	def __init__(self, baseline, acarisModel):
+	def __init__(self, baseline, acarisModel, baselineName, acarisName):
 		self.baseline = baseline
 		self.acarisModel = acarisModel
+		self.baselineName = baselineName
+		self.acarisName = acarisName
+		self.resDir = f"conclusions/{baselineName}_vs_{acarisName}"
+		os.makedirs(self.resDir, exist_ok=True)
 
 	def compare(self, data):
 		uids = list(data["uid"])
@@ -33,16 +47,41 @@ class ACARISComparer:
 		y_true = np.array(y_true)
 		y_pred1 = np.array(y_pred1)
 		probs1 = np.concatenate(probs1)
-		self.compute_metrics(y_true, y_pred1, probs1, classLabels)
+		baselineStat = self.compute_metrics(y_true, y_pred1, probs1, classLabels)
 
 		print("ACARIS metrics:")
-		self.compute_metrics(y_true, y_pred2, probs2, classLabels)
+		acarisStat = self.compute_metrics(y_true, y_pred2, probs2, classLabels)
+
+		print("Statistical tests:")
+		statRes = self.stat_test(baselineStat, acarisStat)
+
+		with open(f"{self.resDir}/conclusions.txt", "w") as f:
+			print(colored("-------------------------\n\n\n\nCONCLUSION\n\n\n\n-------------------------", "yellow"))
+			significant = [metric for metric, p, in statRes if p < 0.05]
+			improved = [metric for metric in significant if acarisStat[metric] > baselineStat[metric] * 1.05]
+
+			f.write("Conclusion:\n\n")
+			if significant:
[…]

### 2023-06-10 dataAnal.py

@@ -27,7 +27,7 @@ def preprocess_msgs(msgs):
 	processedMsgs = []
 	for msg in msgs:
 		words = re.findall(r"\b(?!\d+\b)\w+\b", msg)
-		words = [word.lower() for word in words if word.lower() not in stopWords and "smiling" not in word.lower() and "eyes" not in word.lower() and "face" not in word.lower() and "https" not in word.lower() and "grinning" not in word.lower() and "clyde" not in word.lower() and "unclyde" not in word.lower()]
+		words = [word.lower() for word in words if word.lower() not in stopWords and "smiling" not in word.lower() and "eyes" not in word.lower() and "face" not in word.lower() and "https" not in word.lower() and "grinning" not in word.lower() and "clyde" not in word.lower() and "unclyde" not in word.lower() and "com" != word.lower()]
 		processedMsgs.append(words)
 	return processedMsgs
 

### 2023-06-10 data_loader.py

@@ -67,6 +67,8 @@ def split_data(data, trainRatio, valRatio, filterInsufficient):
 
 		pbar.update()
 
+		# the resulting sets have the following percentages: train: 75%, val: 10%, test: 15%
+
 	print(f"Train columns: {trainData.columns}")
 
 	print(f"Dropped {dropped} rows")

### 2023-06-10 inferDistilBERT.py

@@ -1,10 +1,11 @@
-from transformers import DistilBertTokenizerFast
+from transformers import DistilBertTokenizerFast, pipeline
 import torch
 import sys
 from trainDistilBERT import DistilBertForMulticlassSequenceClassification
 import os
 import numpy as np
 import wandb
+import shap
 
 wandb.init(mode="disabled")
 os.environ["WANDB_MODE"] = "disabled"
@@ -12,9 +13,12 @@ os.environ["WANDB_MODE"] = "disabled"
 class InferACARISBERT:
 	def __init__(self, mdlPath):
 		self.mdlPath = mdlPath
-		self.tokenizer = DistilBertTokenizerFast.from_pretrained("distilbert-base-uncased")
+		self.tokenizer = DistilBertTokenizerFast.from_pretrained(self.mdlPath)
 		self.device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
 		self.model = DistilBertForMulticlassSequenceClassification.from_pretrained(self.mdlPath).to(self.device)
+
+		# TODO: #10 define a custom Transformers pipeline
+		self.classifier = pipeline("sentiment-analysis", model=self.model, tokenizer=self.tokenizer, top_k=None, device=0)
 
 	def prepare_input(self, text):
 		inputs = self.tokenizer(text, truncation=True, padding="max_length", max_length=512, return_tensors="pt").to(self.device)
@@ -25,9 +29,8 @@ class InferACARISBERT:
 		probs = torch.nn.functional.softmax(outputs.logits, dim=-1)
 		return probs.detach().cpu().numpy()
 
-	def infer(self):
-		for text in sys.stdin:
-			text = text.strip()
+	def infer(self, text):
+		if text:
 			inputs = self.prepare_input(text)
 			pred = self.predict(inputs)
 			print(f"Input: {text}\nPrediction: {pred}\n")
@@ -35,8 +38,30 @@ class InferACARISBERT:
 			label = self.model.config.id2label[maxProb[0]]
 			confidence = pred[0][maxProb[0]]
 			print(f"Label: {label}\nConfidence: {confidence}\n")
+		else:
+			for text in sys.stdin:
+				text = text.strip()
+				inputs = self.prepare_input(text)
+				pred = self.predict(inputs)
+				print(f"Input: {text}\nPrediction: {pred}\n")
+				maxProb = np.argmax(pred, axis=-1)
[…]

### 2023-06-10 trainACARIS.py

@@ -20,14 +20,14 @@ from user_embedder import UserEmbedder
 config = {
 	"mdl": "distilbert-base-uncased",
 	"epochs": 2,
-	"batchSize": 14,
+	"batchSize": 32,
 	"maxLen": 512,
-	"warmupSteps": 0.1, # proportion of total steps, NOT absolute
+	"warmupSteps": 0.05, # proportion of total steps, NOT absolute
 	"weightDecay": 0.02,
 	"outputDir": "./output",
 	"earlyStopping": True,
 	"earlyStoppingPatience": 2,
-	"dropout": 0.1,
+	"dropout": 0.2,
 	"initlr": 5e-5,
 	"epsilon": 1e-8
 }
@@ -59,11 +59,11 @@ class DistilBertForMulticlassSequenceClassification(DistilBertForSequenceClassif
 			nn.ReLU(),
 			nn.Linear(512, config.dim), # config.dim.shape = (768,)
 			nn.LayerNorm(config.dim),
-			nn.Dropout(0.5),
+			nn.Dropout(0.1),
 			nn.Linear(config.dim, 512),
 			nn.ReLU(),
 			nn.LayerNorm(512),
-			nn.Dropout(0.5),
+			nn.Dropout(0.1),
 			nn.Linear(512, config.dim)
 		)
 		#self.small = nn.Linear(config.dim * 2, config.dim)
@@ -115,8 +115,7 @@ class ACARISModel:
 		df = dataset.to_pandas()
 		uids = df["uid"].unique()
 
-		# create a dictionary to hold all unique uid embeddings
-		userEmbs = {uid: self.userEmbedder.get_user_embedding(uid) for uid in uids}
+		userEmbs = {uid: self.userEmbedder.get_user_embedding(uid) for uid in uids} # create a dictionary to hold all unique uid embeddings
 
 		def map(x):
 			return {
@@ -181,7 +180,7 @@ class ACARISModel:
 			save_total_limit=5,
 			adam_epsilon=config["epsilon"],
 			report_to="wandb",
-			fp16=True
+			fp16=False
 		)
 		
 		trainer = Trainer(

### 2023-06-13 paper.tex
final ready prelim -- far more work to be done

@@
 
-\title{ACARIS: Improving Conversational AI and Human Social Skills using User Embeddings}
+\title{ACARIS: Attempting to Improve Conversational AI and Human Social Skills using User Embeddings}
 \author{Simon Slamka\\
@@
 None of these methods have proven to be accurate enough (barely reaching 50\% accuracy) for large amounts of complex language, especially casual language that often includes slang, sarcasm, emoji, and similar elements.
-The primary issue was the lack of these methods' ability to capture semantical and contextual aspects of our dataset.
+The primary issue was the lack of these methods' ability to capture semantic and contextual aspects of our dataset.
 SVMs, DTs, LogReg, and RFs weren't built specifically for sequential data.
@@
 \end{equation}
-The FFNN contains 3 layers, each with a ReLU activation function, a layer normalization, and dropout for regularization.
-The first linear (dense) layer is a function $y = xw + b$, where $x$ is a user embedding vector, that takes in the $d_e$-dimensional user embedding and learns to transform it to a dimensionality of 512.
+The FFNN contains 3 layers, each with a ReLU activation, a layer normalization, and dropout for regularization.
+The first linear (dense) layer is a function $y = xw + b$, where $x$ is a user embedding vector that takes in the $d_e$-dimensional user embedding and learns to transform it to a dimensionality of 512.
 After the first linear transformation, ReLU will return 0 if its input is negative, and the value of the input if it's 0 or positive.
@@
 \\
-The following is the model definition:\\
+The following is the model definition (shared with permission from OngakkenAI):\\
 
@@
 To associate the user embedding with each token, we need to repeat it along a third dimension, which we need to add, making the user embedding a 3D tensor.
-We first add a singleton dimension to the position 1 using the unsqueeze() method, changing the shape to $(batchSize, 1, userEmbSize)$, and subsequently repeat the user embedding along this dimension using the repeat() method, changing the second dimension from $1$ to $seqLen$ (input sequence length), as such $(batchSize, seqLen, userEmbSize)$.
+We first add a singleton dimension to the position 1 using the unsqueeze() method, changing the shape to $(batchSize, 1, userEmbSize)$, and subsequently, repeat the user embedding along this dimension using the repeat() method, changing the second dimension from $1$ to $seqLen$ (input sequence length), as such $(batchSize, seqLen, userEmbSize)$.
 The unsqueeze() method doesn't affect the data inside the tensor, only its shape.
@@
 \subsection{Training with user embeddings}
-For each training step, we pass the concatenated embeddings $e_\textnormal{joint}$ through the model and compute the cross-entropy loss $L$ (negative logarithmic likelihood).
-Then, we backpropagate gradients from the loss to the model parameters and update the parameters using Adam.
-The model thus learns to associate every message $m$ with a user embedding $e_u$ and a sentiment label $y$.
+For each training step, we retrieve the underlying DistilBERT model's output at position 0 and store it in $hidden_state$.
+We then pass the user embedding $e_u$ to the user embedding FFNN, which returns the user embedding's $e'_u$.
+Subsequently, we initialize a variable $userEmbsRep$, as explained above.
+After concatenating the user embeddings $e'_u$ with the hidden state, we supply the resulting $pooled_output$ to the final classifier, returning logits.
+Having logits, we can calculate loss, which we do using the negative logaritmic likelihood loss function (CrossEntropyLoss).
+Lastly, we return the loss and logits or a SequenceClassifierOutput object (depending on the value of return\_dict).\\
 
@@
 Instead, they are pre-computed during data preprocessing and stored in a .pt file, one file per user.
+As such, we can reuse them later, without the need to run feature extraction again.
 We repeat training every week, using new data from the previous week to update the user embeddings $e_u$.
@@
 We use the same model, DistilBERT, but without user embeddings $e_u$.
-We fine-tune both models on the same dataset and compared their performance on the same test set.\\\\
+We fine-tune both models on the same dataset and compare their performance on the same test set.\\\\
 The base model performed as follows:
@@
 Another area of improvement, in our opinion, is the concatenation operation.
-We believe that summation may offer different results, and will try to implement it in the future.
+We believe that summation with word embeddings instead of concatenation may offer different results, and will try to implement it in the future.
 Finally, and this is the most important factor, is the lack of user-specific data.
-We don't presently have sufficient messages for many users to train a model that generalizes well.
+We don't presently have sufficient messages for many users to train a model that generalizes well, most likely due to our aggressive filtering procedure (all users with less than 25 messages and messages of less than 25 characters are discarded).
 We suspect that this is the main reason why our model failed to outperform the baseline model.

### 2023-06-13 trainACARIS.py

@@ -84,7 +84,8 @@ class DistilBertForMulticlassSequenceClassification(DistilBertForSequenceClassif
 		pooled_output = self.dropout(pooled_output)
 		logits = self.classifier(pooled_output)
 
-		loss = None
+		loss = None # the fuck did this come from???!
+
 		if labels is not None:
 			lossFct = nn.CrossEntropyLoss()
 			loss = lossFct(logits.view(-1, self.num_labels), labels.view(-1))
